\documentclass[12pt]{article}

\textheight= 9in
\textwidth= 6.5in

%\hoffset = -1.1in
%\voffset= -0.75in
%\voffset= -1.25in
%\voffset= -.75in
%\voffset=-1.40in
\voffset=-.8in
\hoffset = -.55in

\parindent= 0.0in
\pagestyle{empty}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}















 \newcommand\kreis[1]{\ensuremath{\mathbin{\settowidth{\dimen6}{\mbox{$\bigcirc$}}%
              \makebox[0pt][l]{$\bigcirc$}\makebox[\dimen6]{#1}}}}
















\begin{document}




\centerline{\bf \large  STATEMENT OF RESEARCH}
\vspace{0.2in}
\centerline{ JENNIFER M.\ GORSKY}
\vspace{0.3in}







\noindent
{\bf Well-posedness of nonlinear evolution equations in Sobolev spaces}.
The main  focus of my research thus far has been the
  periodic initial value problem for a modified
Camassa-Holm (mCH) equation
\begin{equation}
\label{eq:EpsmCH}
\partial_t u + u\partial_x u +\varepsilon \partial^3_x u +
(1-\partial_x^2)^{-1}\partial_x[u^2+\frac 12(\partial_x u)^2]= 0,
\end{equation}
\vskip -.4in
\begin{equation}
\label{eq:EpsmCHdata} u(x, 0) = \varphi (x),\quad
\ t \in \mathbb{R},  \;\; \ x \in \mathbb{T}.
\end{equation}
Equation (\ref{eq:EpsmCH}) is obtained by adding the term
$\varepsilon \partial^3_x u$
to the Camassa-Holm (CH) equation.  Inserting this
stronger dispersive term and investigating
both the modified equation and its (dispersive) limit as $\varepsilon
\rightarrow 0$, has  been motivated by other
works in the  literature.
For instance, in  [LL] Lax and Levermore considered
the zero dispersion limit of the initial value problem for the KdV equation
$\partial_t u + u\partial_x u +\varepsilon \partial^3_x u=0$.


\quad For $\varepsilon = 1$, Himonas and Misio\l ek proved
well-posedness of (\ref{eq:EpsmCH})--(\ref{eq:EpsmCHdata}) for initial data
in the Sobolev space $H^s(\mathbb{T})$, $s>1/2$
(see [HM1]), by extending the techniques Bourgain used to prove
well-posedness
  for the KdV equation for $s\ge0$ (see [B]).  I have
improved this result by   showing  local well-posedness of
(\ref{eq:EpsmCH})--(\ref{eq:EpsmCHdata}) for $\varphi \in H^s(\mathbb{T})$,
$s\ge 1/2$.  For this, I have extended the method
used by Kenig, Ponce and Vega for  proving well-posedness for the KdV equation
when $s\ge -1/2$ (see [KPV]).   Using this alternative approach enabled 
me to lower
the Sobolev exponent to $s=1/2$.
Also, in my dissertation I have shown  that the bilinear estimates used
previously in proving well-posedness fail when $s<1/2$.
This indicates that  $s=1/2$ might be the critical exponent for
local well-posedness of the mCH equation in Sobolev spaces.
However, this must be proved, and this is thus one of the
research problems I would like to work on.
Ill-posedness results for the KdV and CH equations rely on
explicit traveling wave solutions.
Therefore, as a starting point, I intend
to study the ODE that traveling wave
solutions of the mCH equation must satisfy.


\quad   Studying more general evolution equations with stronger
nonlinearities is also of interest. For example,  Himonas and Misio\l ek
have shown that the Cauchy problem
\begin{equation}
\label{eq:HigherOrdermCH}
\partial_t u - \partial^2_x \partial_t u + \partial^{2j+1}_x u
-\partial^{2j+3}_x u + 3u
\partial_x u - 2\partial_x u \partial^2_x u - u \partial^3_x u = 0,
\end{equation}
\vskip -.4in
\begin{equation}
\label{eq:HigherOrdermCHdata} u(x, 0) = \varphi (x),\quad
\ t \in \mathbb{R},  \;\; \ x \in \mathbb{T},
\end{equation}
is locally well-posed for $s>\frac{2-j}{2}$, where $j$ is a positive
integer (see [HM2]).  I would like to explore proving this result for a
lower
$s$.

\vskip .1in
\noindent
{\bf {The Cauchy Problem for Analytic Initial Data}.}
  Another problem I am interested in is the
study of the Cauchy problem (\ref{eq:EpsmCH})--(\ref{eq:EpsmCHdata})
when the initial data are analytic. 
Is the solution
then also analytic in the space variable?
What about analyticity in the time variable?



\quad   In collaboration with Alex Himonas, I have constructed non-analytic
solutions to the Cauchy problem for the generalized KdV equation  with
appropriate analytic initial data.   It is well-known that solutions to the
KdV equation are analytic in the space variable, but 
not 



 





 \newpage

{\bf Jennifer M.\ Gorsky, page 2}






\vskip 0.3in



in the time
variable. The question then is the following: Is the situation concerning
analyticity of solutions to the mCH equation similar to that of the KdV
equation?   Concerning analyticity in the space variable, the answer is
yes.  I have recently shown, in a preprint entitled {\em The Cauchy problem
for a modified Camassa-Holm equation with analytic initial data}, that
(\ref{eq:EpsmCH})--(\ref{eq:EpsmCHdata}) with analytic initial data is
analytic in the space variable $x$ for all time.  

\quad  I plan to continue my investigation of the regularity of solutions
problem for other nonlinear evolution
equations with analytic initial data.



\vskip 0.1in
\noindent
{\bf {Numerical Analysis.}}
I am also interested in investigating the
behavior of solutions of (\ref{eq:EpsmCH})--(\ref{eq:EpsmCHdata}) as
$\varepsilon$ goes to zero.
For a given $\varphi$, a natural question to ask is whether solutions
of (\ref{eq:EpsmCH})--(\ref{eq:EpsmCHdata}) converge to solutions of
the CH Cauchy problem as $\varepsilon \rightarrow 0$.  Using
numerical methods, I have explored this question.
My results indeed indicate that for certain
initial data, solutions of (\ref{eq:EpsmCH})--(\ref{eq:EpsmCHdata}) converge
to solutions of the CH Cauchy problem as $\varepsilon \rightarrow 0$.  I am
interested in strengthening my numerical findings by proving  results
which state that solutions of (\ref{eq:EpsmCH})--(\ref{eq:EpsmCHdata})
converge to solutions of the CH Cauchy problem for appropriate initial data.







\begin{thebibliography}{ABCDE}

\bibitem[B]{b} J. Bourgain, {\em Fourier transform restriction
phenomena  for certain lattice subsets  and applications to
nonlinear evolution equations.  Part 2: KdV equation}, Geom.
Funct. Anal. {\bf 3} (1993).

\bibitem[CKSTT]{ckstt1} J. Colliander, M. Keel, G. Staffilani,
H. Takaoka, and T. Tao,
{\em Sharp global well-posedness for KdV and modified KdV on $\mathbb R$ and
$\mathbb T$},
    J. Amer. Math. Soc. {\bf 16}, No. 3, (2003), 705--749.


\bibitem[HM1]{hm} A. A. Himonas and G. Misio\l ek,  {\em Well-posedness of
the Cauchy problem for a shallow water equation on the circle},  Journal of
Differential Equations {\bf 161} (2000).


\bibitem[HM2]{hm} A. A. Himonas and G. Misio\l ek,  {\em The
Cauchy problem for a shallow water type equation},  Comm.
Partial Differential Equations {\bf 23} (1998).

\bibitem[KPV]{kpv3} C. Kenig, G. Ponce and L. Vega,  {\em A bilinear
estimate with applications to the KdV equation},
Journal A.M.S. {\bf 9} (1996).

\bibitem[LL]{kpv3} P. Lax and D. Levermore,  {\em The zero dispersion
limit for the Korteweg-de Vries (KdV) equation},  Proc. Nat. Acad.
Sci. U.S.A. {\bf 76} (1979).



\end{thebibliography}




\end{document}





