\documentclass[12pt]{letter}
\usepackage[top=0.3cm,bottom=0.3cm]{geometry}
\renewcommand{\baselinestretch}{1.1} %increases vert spacing of text
\synctex=1
\name{David Karapetyan}
\signature{\vspace{-0.5cm}David Karapetyan}
%\longindentation=0pt
\date{\vspace{0.5cm}\flushleft \today}
\begin{document}

\begin{letter}{University of Rochester \\
Department of Mathematics \\
Hylan 917, RC Box 270138 \\
Rochester, NY 14627}
        \begin{center}
{\bf {\Large David Karapetyan}}
\end{center}

\begin{center}
{255 Hurley Hall, Notre Dame, IN 46556  $\bullet$
202-460-5173 $\bullet$ dkarapet@nd.edu
}
\end{center}
\hrule

\opening{Dear Members of the Search Committee:\\}
%
%
I wish to apply for a Visiting Assistant Professor position at the University of
Rochester. I am currently working in \textbf{PDEs} and in
particular \textbf{nonlinear evolution equations} as a student of Alex Himonas
at the University of Notre Dame, and I anticipate
completing my Ph.D. in May, 2012. I have been studying the hyperelastic rod (HR)
equation, an important nonlinear evolution equation modeling finite-length and
small-amplitude axial deformation waves in thin cylindrical rods. I recently
published a paper on this equation, entitled {\it ``Non-uniform dependence and
well-posedness for the hyperelastic rod equation''}. I have also recently
completed a preprint entitled {\it ``H\"older continuity of the data to solution
map for HR in the weak topology''}. I would like the opportunity to join your
department and interact with your faculty in PDE and the applied mathematics
group, including Professors Geba and Greenleaf among many others.

I have taught freshman calculus twice at Notre Dame, and scored in the top 10\%
in all meaningful categories the second time around, in particular teaching
clarity, preparation, and ability to promote mastery of the subject matter. I
have also given many talks at conferences and seminars at a number of
universities. 

I am committed to pursuing a research career in academia, but also have a love
of teaching. If you have any questions, please do not hesitate to ask. Thank you for your time and consideration. 

\closing{Sincerely,}


\end{letter}

\end{document}
