\documentclass[12pt]{letter}
\usepackage[top=0.3cm,bottom=0.3cm]{geometry}
\renewcommand{\baselinestretch}{1.1} %increases vert spacing of text
\synctex=1
\name{David Karapetyan}
\signature{\vspace{-0.5cm}David Karapetyan}
%\longindentation=0pt
\date{\vspace{0.5cm}\flushleft \today}
\begin{document}

\begin{letter}{D. E. Shaw \& Co., L.P. \\
39th Floor, Tower 45 \\
120 West 45th Street \\
New York, NY 10036
}
    \begin{center}
{\bf {\Large David Karapetyan}}
\end{center}

\begin{center}
{255 Hurley Hall, Notre Dame, IN 46556  $\bullet$
202-460-5173 $\bullet$ dkarapet@nd.edu
}
\end{center}
\hrule

\opening{Dear Members of the Hiring Committee:\\}
%
%
I wish to apply for a quantitative analyst position at D. E. Shaw. I am
currently working in \textbf{Partial Differential Equations} and in particular
\textbf{nonlinear evolution equations} at the University of Notre Dame, and I
anticipate completing my Ph.D.  in May, 2012. I have been studying the
hyperelastic rod (HR) equation, an important nonlinear evolution equation
modeling finite-length and small-amplitude axial deformation waves in thin
cylindrical rods. I recently published a paper on this equation, entitled {\it
``Non-uniform dependence and well-posedness for the hyperelastic rod
equation''}. I have also recently completed a preprint entitled {\it ``H\"older
continuity of the data to solution map for HR in the weak topology''}. My
background in applied mathematics, and in particular my experience coding
numerical algorithms in C++ and MATLAB to aid my research, have given me the
tools needed to build a career in finance.

I have taught freshman calculus twice at Notre Dame, and scored in the top 10\%
in all meaningful categories the second time around, in particular teaching
clarity, preparation, and ability to promote mastery of the subject matter. I
have also given many talks at conferences and seminars at a number of
universities. My experience teaching and presenting my research have equipped
me with the communication skills necessary to work in a team effectively. 

Prior to enrolling at Notre Dame, I worked in Washington D.C. as a research
associate for both the Institute for Defense Analyses and the Battelle Memorial
Institute. My numerical and consulting experience at these two think tanks are
detailed in my resume, and prepared me for life at Notre Dame and beyond. 

If you have any questions, please do not hesitate to ask. It would be a pleasure to
interview with you, and I hope to hear from you soon. Thank you for your time
and consideration. 

\closing{Sincerely,}


\end{letter}

\end{document}
