\chapter*{Acknowledgments}
I would like to thank my advisor, Professor Alex Himonas,
for his support and guidance. I am also grateful to the math department and the  Arthur J. Schmitt
Foundation for supporting my graduate studies. 

Thanks also to Gerard Misio{\l}ek, who was always ready to answer the
random analysis question or talk about the arts. To Professors Yongtao
Zhang and Bei Hu, for serving on my defense committee, and for suggesting
many interesting research projects. To Professor Gerson
Petronilho, for the many talks he has given in the analysis seminar, and
his patience in collaborating with a junior mathematician. I am also
indebted to my friend and collaborator Professor Dan Geba, who is one of
the finest human beings I have ever known. He's also not too shabby at
tennis. 

Many thanks to my officemates Yen Huang and Wenrui Hao, who were always
willing to discuss mathematics with me when we weren't horsing around. I
must also thank Katie Grayshan for her friendship and many useful
discussions, which helped me identify and shore up my weaknesses. 

Thanks to Beth VerVelde, who understood me better than most, and is too
wise for her own good. To my friends back home, thanks goes to Cynthia
Ramirez, who always felt guilty whenever I was sent to voicemail, and
called me back as soon as possible. Your patience and loyalty helped me
persevere, and will not be forgotten. To Amelda zemer, your kindnesses and
enormous heart have given me the strength to never break, no matter the
adversity or general nonsense I may encounter.

Lastly, thanks to my mom, Satenik Antonian, who has always had my best
interests at heart, and has never wavered in her support and love. You have
suffered more than most, yet take it stoically, with great grace, honor,
and strength.    

