\documentclass[12pt,reqno]{amsbook}
%
%
\usepackage[utf8]{inputenc}
%\usepackage{showkeys}
\usepackage[T1]{fontenc} %otherwise have font issues
\usepackage{lmodern} %this with above font packages give us all possible diacritics
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{appendix}
\usepackage{amssymb}
\usepackage{cancel}  %for cancelling terms explicity on pdf
\usepackage{yhmath}   %makes fourier transform look nicer, among other things
\usepackage{framed}  %for framing remarks, theorems, etc.
\usepackage{appendix}
\synctex=1
\usepackage{enumerate} %to change enumerate symbols
\usepackage[margin=2.5cm]{geometry}  %page layout
\setcounter{tocdepth}{1} %must come before secnumdepth--else, pain
\setcounter{secnumdepth}{1} %number only sections, not subsections
%\usepackage[pdftex]{graphicx} %for importing pictures into latex--pdf compilation
\numberwithin{section}{chapter} 
\numberwithin{equation}{chapter}  %eliminate need for keeping track of counters
%\numberwithin{figure}{section}
%\setlength{\parindent}{0in} %no indentation of paragraphs after section title
%\setlength{\parskip}{0.1in} %ensure that blank source code lines generate space
% in amsbook class and others. Automatic for amsart
\renewcommand{\baselinestretch}{1.1} %increases vert spacing of text
%\renewcommand{\subsection}{\textbf} %temporary fix--subsection indents in
%amsbook, and want to disable it
%
\usepackage{hyperref}
\hypersetup{colorlinks=true,
linkcolor=blue,
citecolor=blue,
urlcolor=blue,
}
%\usepackage[alphabetic, initials, msc-links]{amsrefs} %for the bibliography; uses cite pkg. Must be loaded after hyperref, otherwise doesn't work properly (conflicts with cref in particular)
\usepackage{cleveref} %must be last loaded package to work properly
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{prop}[theorem]{Proposition}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{no}[theorem]{Notation}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{examp}{Example}[section]
\newtheorem {exercise}[theorem]{Exercise}
\newcommand{\ds}{\displaystyle}
\newcommand{\ts}{\textstyle}
\newcommand{\nin}{\noindent}
\newcommand{\rr}{\mathbb{R}}
\newcommand{\nn}{\mathbb{N}}
\newcommand{\zz}{\mathbb{Z}}
\newcommand{\cc}{\mathbb{C}}
\newcommand{\ci}{\mathbb{T}}
\newcommand{\zzdot}{\dot{\zz}}
\newcommand{\wh}{\widehat}
\newcommand{\p}{\partial}
\newcommand{\ee}{\varepsilon}
\newcommand{\vp}{\varphi}
\newcommand{\wt}{\widetilde}
%
%
\theoremstyle{remark}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{example}{Example}[section]
%
%
%
\newcommand{\uol}{u^\omega_\lambda}
\newcommand{\lbar}{\bar{l}}
\renewcommand{\l}{\lambda}
\newcommand{\R}{\mathbb R}
\newcommand{\RR}{\mathcal R}
\newcommand{\al}{\alpha}
\newcommand{\ve}{q}
\newcommand{\tg}{{tan}}
\newcommand{\m}{q}
\newcommand{\N}{N}
\newcommand{\ta}{{\tilde{a}}}
\newcommand{\tb}{{\tilde{b}}}
\newcommand{\tc}{{\tilde{c}}}
\newcommand{\tS}{{\tilde S}}
\newcommand{\tP}{{\tilde P}}
\newcommand{\tu}{{\tilde{u}}}
\newcommand{\tw}{{\tilde{w}}}
\newcommand{\tA}{{\tilde{A}}}
\newcommand{\tX}{{\tilde{X}}}
\newcommand{\tphi}{{\tilde{\phi}}}
%\renewcommand{\qed}{\qquad \qedsymbol} %for proof env qed symbol
%\renewcommand \thepart{\Roman{part}} %change part labeling to Roman
%numeral--not needed for memoir
\renewcommand{\cref}{\Cref} %capitalize option for cleveref doesn't work on all
%computers


\begin{document}
\frontmatter
\title{Notes}
\author{David Karapetyan}
%\address{Department of Mathematics, University of Notre Dame, Notre Dame, IN 46556}
%\email{dkarapet@nd.edu}

\date{}

\maketitle
\tableofcontents
\mainmatter
%\part{Strongly Dispersive Equations}
%\include{mnls/mnls}
%\include{nls-l4/nls-l4}
%\include{dnls/dnls}
%\include{kdv/kdv}
%\include{knls/knls}
%\include{mkdv/mkdv}
%\include{nls-gevrey/nls-gevrey}
%\part{Weakly Dispersive Equations}
\include{hr/hr}
\part{Appendix}
%
\include{ode-thm/ode-thm}
%
\backmatter
\providecommand{\bysame}{\leavevmode\hbox to3em{\hrulefill}\thinspace}
\providecommand{\MR}{\relax\ifhmode\unskip\space\fi MR }
% \MRhref is called by the amsart/book/proc definition of \MR.
\providecommand{\MRhref}[2]{%
  \href{http://www.ams.org/mathscinet-getitem?mr=#1}{#2}
}
\providecommand{\href}[2]{#2}
\begin{thebibliography}{HKM09}

\bibitem[BBM72]{Benjamin_1972_Model-equations}
T.~B. Benjamin, J.~L. Bona, and J.~J. Mahony, \emph{Model equations for long
  waves in nonlinear dispersive systems}, Philos. Trans. Roy. Soc. London Ser.
  A \textbf{272} (1972), no.~1220, 47--78.

\bibitem[BC07]{Bressan_2007_Global-conserva}
A.~Bressan and A.~Constantin, \emph{Global conservative solutions of the
  camassa-holm equation}, Arch. Ration. Mech. Anal. \textbf{183} (2007), no.~2,
  215--239.

\bibitem[BCK06]{Bendahmane_2006_Hsp-1-perturbat}
M.~Bendahmane, G.~M. Coclite, and K.~H. Karlsen,
\emph{$H^1$-perturbations of smooth solutions for a weakly dissipative
  hyperelastic-rod wave equation}, Mediterr. J. Math. \textbf{3} (2006),
  no.~3-4, 419--432.

\bibitem[Ben72]{Benjamin_1972_The-stability-o}
T.~B. Benjamin, \emph{The stability of solitary waves}, Proc. Roy. Soc.
  (London) Ser. A \textbf{328} (1972), 153--183.

\bibitem[BT09]{Bona_2009_Sharp-well-pose}
J.~L. Bona and N.~Tzvetkov, \emph{Sharp well-posedness results for the bbm
  equation}, Discrete Contin. Dyn. Syst. \textbf{23} (2009), no.~4, 1241--1252.

\bibitem[CCT03]{Christ_2003_Asymptotics-fre}
M.~Christ, J.~Colliander, and T.~Tao, \emph{Asymptotics, frequency modulation,
  and low regularity ill-posedness for canonical defocusing equations}, Amer.
  J. Math. \textbf{125} (2003), no.~6, 1235--1293.

\bibitem[CHK05]{Coclite_2005_Global-weak-sol}
G.~M. Coclite, H.~Holden, and K.~H. Karlsen, \emph{Global weak solutions to a
  generalized hyperelastic-rod wave equation}, SIAM J. Math. Anal. \textbf{37}
  (2005), no.~4, 1044--1069 (electronic).

\bibitem[CS00]{Constantin_2000_Stability-of-a-}
A.~Constantin and W.~A. Strauss, \emph{Stability of a class of solitary waves
  in compressible elastic rods}, Phys. Lett. A \textbf{270} (2000), no.~3-4,
  140--148.

\bibitem[Dai98]{Dai_1998_Model-equations}
H.-H. Dai, \emph{Model equations for nonlinear dispersive waves in a
  compressible mooney-rivlin rod}, Acta Mech. \textbf{127} (1998), no.~1-4,
  193--207.

\bibitem[DDH00]{Dai_2000_Head-on-collisi}
H.-H. Dai, S.~Dai, and Y.~Huo, \emph{Head-on collision between two solitary
  waves in a compressible mooney-rivlin elastic rod}, Wave Motion \textbf{32}
  (2000), no.~2, 93--111.

\bibitem[DH00]{Dai_2000_Solitary-shock-}
H.-H. Dai and Y.~Huo, \emph{Solitary shock waves and other travelling waves in
  a general compressible hyperelastic rod}, R. Soc. Lond. Proc. Ser. A Math.
  Phys. Eng. Sci. \textbf{456} (2000), no.~1994, 331--363.

\bibitem[Die69]{Dieudonne_1969_Foundations-of-}
J.~Dieudonn{\'e}, \emph{Foundations of modern analysis}, 1969.

\bibitem[Fol99]{Folland_1999_Real-analysis}
G.~B. Folland, \emph{Real analysis}, 1999.

\bibitem[HK09]{Himonas:2009fk}
A.~Himonas and C.~E. Kenig, \emph{Non-uniform dependence on initial data for
  the ch equation on the line}, Differential Integral Equations \textbf{22}
  (2009), no.~3-4, 201--224.

\bibitem[HKM09]{Himonas_2009_Non-uniform-dep-per}
A.~Himonas, C.~E. Kenig, and G.~Misiolek, \emph{Non-uniform dependence for the
  periodic ch equation.}, To appear in Communications in Partial Differential
  Equations (2009).

\bibitem[HM01]{Himonas_2001_The-Cauchy-prob}
A.~Himonas and G.~Misiolek, \emph{The cauchy problem for an integrable
  shallow-water equation}, Differential Integral Equations \textbf{14} (2001),
  no.~7, 821--831.

\bibitem[HM05]{Himonas:2005kx}
\bysame, \emph{High-frequency smooth solutions and well-posedness of the
  camassa-holm equation}, Int. Math. Res. Not. (2005), no.~51, 3135--3151.

\bibitem[HM09]{Himonas_2009_Non-uniform-dep-euler}
\bysame, \emph{Non-uniform dependence on initial data of solutions to the euler
  equations of hydrodynamics}, Communications in Mathematical Physics (2009).

\bibitem[HMP07]{Himonas_2007_Non-uniform-con}
A.~Himonas, G.~Misiolek, and G.~Ponce, \emph{Non-uniform continuity in {\$}h\^
  1{\$} of the solution map of the ch equation}, Asian J. Math. \textbf{11}
  (2007), no.~1, 141--150.

\bibitem[HR07]{Holden_2007_Global-conserva}
H.~Holden and X.~Raynaud, \emph{Global conservative solutions of the
  generalized hyperelastic-rod wave equation}, J. Differential Equations
  \textbf{233} (2007), no.~2, 448--484.

\bibitem[Jos98]{Jost-1998-Postmodern-analysis}
J.~Jost, \emph{Postmodern analysis}, 1998.

\bibitem[Kat75]{Kato_1975_Quasi-linear-eq}
T.~Kato, \emph{Quasi-linear equations of evolution, with applications to
  partial differential equations}, 1975, pp.~25--70. Lecture Notes in Math.,
  Vol. 448.

\bibitem[Kna05a]{Knapp:2005rm}
A.~Knapp, \emph{Advanced real analysis}, 2005.

\bibitem[Kna05b]{Knapp:2005yg}
\bysame, \emph{Basic real analysis}, 2005.

\bibitem[KPV01]{Kenig_2001_On-the-ill-pose}
C.~E. Kenig, G.~Ponce, and L.~Vega, \emph{On the ill-posedness of some
  canonical dispersive equations}, Duke Math. J. \textbf{106} (2001), no.~3,
  617--633.

\bibitem[KT05]{Koch_2005_Nonlinear-wave-}
H.~Koch and N.~Tzvetkov, \emph{Nonlinear wave interactions for the benjamin-ono
  equation}, Int. Math. Res. Not. (2005), no.~30, 1833--1847.

\bibitem[Len06]{Lenells_2006_Traveling-waves}
J.~Lenells, \emph{Traveling waves in compressible elastic rods}, Discrete
  Contin. Dyn. Syst. Ser. B \textbf{6} (2006), no.~1, 151--167 (electronic).

\bibitem[LO00]{Li_2000_Well-posedness-}
Y.~A. Li and P.~J. Olver, \emph{Well-posedness and blow-up solutions for an
  integrable nonlinearly dispersive model wave equation}, J. Differential
  Equations \textbf{162} (2000), no.~1, 27--63.

\bibitem[Mus07]{Mustafa_2007_Global-conserva}
O.~G. Mustafa, \emph{Global conservative solutions of the hyperelastic rod
  equation}, Int. Math. Res. Not. IMRN (2007), no.~13, Art. ID rnm040, 26.

\bibitem[Ols06]{Olson_2006_Non-uniform-dep}
E.~Olson, \emph{Non-uniform dependence on initial data for a family of
  non-linear evolution equations}, Differential Integral Equations \textbf{19}
  (2006), no.~10, 1081--1102.

\bibitem[RB01]{Rodriguez-Blanco_2001_On-the-Cauchy-p}
G.~Rodr\'iguez-Blanco, \emph{On the cauchy problem for the camassa-holm
  equation}, Nonlinear Anal. \textbf{46} (2001), no.~3, Ser. A: Theory Methods,
  309--327.

\bibitem[Rud76]{Rudin:1976uq}
W.~Rudin, \emph{Principles of mathematical analysis}, 1976.

\bibitem[Tay91]{Taylor_1991_Pseudodifferent}
M.~E. Taylor, \emph{Pseudodifferential operators and nonlinear pde}, vol. 100,
  1991.

\bibitem[Tay95]{Taylor:1995kx}
\bysame, \emph{Partial differential equations i, basic theory}, vol. 115, 1995.

\bibitem[Yin03]{Yin_2003_On-the-Cauchy-p}
Z.~Yin, \emph{On the cauchy problem for a nonlinearly dispersive wave
  equation}, J. Nonlinear Math. Phys. \textbf{10} (2003), no.~1, 10--15.

\bibitem[Yos80]{Yosida:1980fk}
K.~Yosida, \emph{Functional analysis}, vol. 123, 1980.

\bibitem[Zho05]{Zhou_2005_Local-well-pose}
Y.~Zhou, \emph{Local well-posedness and blow-up criteria of solutions for a rod
  equation}, Math. Nachr. \textbf{278} (2005), no.~14, 1726--1739.

\end{thebibliography}
%\bibliography{/Users/davidkarapetyan/math/bib-files/references}
%\bibliographystyle{amsalpha-custom}
%
%If want reference in normal size, do \begin{biblist}[\normalsize]
\end{document}
