\ProvidesFile{template.tex}
\documentclass[final, 12pt, noinfo]{nddiss2e}
                     % Available options are
                     % (a) draft + 10pt/11pt/12pt + twoadvisors + textrefs
                     % (b) review + noinfo + twoadvisors + textrefs
                     % (c) final + noinfo + twoadvisors + textrefs
\let\bibsection\relax 

\usepackage{titlesec}
\titleformat{\chapter}[display]{\centering}
{\chaptertitlename\ \thechapter}{20pt}{\uppercase} %capitalize
%chapters--required by thesis format
\usepackage{titletoc}  %capitalize chapters in toc--required by thesis
\titlecontents{chapter}
[0pt]
{\addvspace{1pc}%
\normalfont}%
{\contentsmargin{0pt}%
\normalfont
\makebox[0pt][r]{\huge\thecontentslabel\enspace}%
\uppercase}
{\contentsmargin{0pt}%
\uppercase}
{}
[\addvspace{0.1pc}]

\setcounter{tocdepth}{1} %must come before secnumdepth--else, pain
\setcounter{secnumdepth}{1} %number only sections, not subsections
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl} 
\usepackage{fix-cm} %allow arbitrary size fonts
\usepackage{type1ec} %ditto
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage[showonlyrefs=true]{mathtools} %amsmath extension package
\usepackage{cancel}  %for cancelling terms explicity on pdf
%\usepackage{yhmath}   %makes fourier transform look nicer, among other things
\usepackage{framed}  %for framing remarks, theorems, etc.
\usepackage{appendix}
\synctex=1
\usepackage{enumerate} %to change enumerate symbols
\usepackage[initials]{amsrefs} %for the bibliography; uses cite pkg. Must be loaded after hyperref, otherwise doesn't work properly (conflicts with cref in particular)
\usepackage{hyperref}
\hypersetup{colorlinks=true,
linkcolor=blue,
citecolor=blue,
urlcolor=blue,
}
\usepackage{cleveref} %must be last loaded package to work properly
\renewcommand{\cref}{\Cref}
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{prop}[theorem]{Proposition}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{no}[theorem]{Notation}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{examp}{Example}[section]
\newtheorem {exercise}[theorem] {Exercise}

\newcommand{\ds}{\displaystyle}
\newcommand{\ts}{\textstyle}
\newcommand{\nin}{\noindent}
\newcommand{\rr}{\mathbb{R}}
\newcommand{\nn}{\mathbb{N}}
\newcommand{\zz}{\mathbb{Z}}
\newcommand{\cc}{\mathbb{C}}
\newcommand{\ci}{\mathbb{T}}
\newcommand{\zzdot}{\dot{\zz}}
\newcommand{\wh}{\widehat}
\newcommand{\p}{\partial}
\newcommand{\ee}{\varepsilon}
\newcommand{\vp}{\varphi}
\newcommand{\wt}{\widetilde}
%
%
%
%
%
%\makeatletter \renewenvironment{proof}[1][\proofname] {\par\pushQED{\qed}\normalfont\topsep6\p@\@plus6\p@\relax\trivlist\item[\hskip\labelsep\bfseries#1\@addpunct{.}]\ignorespaces}{\popQED\endtrivlist\@endpefalse} \makeatother%
%%makes proof environment bold instead of italic
\newcommand{\uol}{u^\omega_\lambda}
\newcommand{\lbar}{\bar{l}}
\renewcommand{\l}{\lambda}
\newcommand{\R}{\mathbb R}
\newcommand{\RR}{\mathcal R}
\newcommand{\al}{\alpha}
\newcommand{\ve}{q}
\newcommand{\tg}{{tan}}
\newcommand{\m}{q}
\newcommand{\N}{N}
\newcommand{\ta}{{\tilde{a}}}
\newcommand{\tb}{{\tilde{b}}}
\newcommand{\tc}{{\tilde{c}}}
\newcommand{\tS}{{\tilde S}}
\newcommand{\tP}{{\tilde P}}
\newcommand{\tu}{{\tilde{u}}}
\newcommand{\tw}{{\tilde{w}}}
\newcommand{\tA}{{\tilde{A}}}
\newcommand{\tX}{{\tilde{X}}}
\newcommand{\tphi}{{\tilde{\phi}}}
\renewcommand{\qed}{\qquad \qedsymbol}
%\renewcommand{\chaptername}{CHAPTER}
\begin{document}

\frontmatter         % All the items before Chapter 1 go in ``frontmatter''

\title{}            % Title of Work
\author{David Karapetyan}           % Author's name
\work{Dissertation}             % ``Dissertation'' or ``Thesis''
\degprior{ }         % All prior degrees
\degaward{ }         % Degree you're aiming for
\advisor{Alex Himonas}          % Advisor's name
 % \secondadvisor{ } % Second advisor, if used option ``twoadvisors''
\department{Department of Mathematics, University of Notre Dame}       % Name of the department

\maketitle           % The title page is created now

 % \copyrightholder{ } % If you're not the copyright holder
 % \copyrightyear{ }   % If the copyright is not for the current year
 % \makecopyright      % If not making your work public domain
                       % uncomment out \makecopyright
 % \makepublicdomain   % Uncomment this to make your work public domain

 % \begin{abstract}
 % \end{abstract}
 %                         % Either place the text between begin/end, or
 % \include{abstract}  % put it in a file to be included

 % \renewcommand{\dedicationname}{\mbox{}} % Replace \mbox{} if you want
                                           % something else
 % \begin{dedication}
 % \end{dedication}
 %                       % Use one of the two choices to add dedication text
 % \include{dedication}

\tableofcontents
%\listoffigures
%\listoftables

 %% \renewcommand{\symbolsname}{newsymname} % Replace ``newsymname'' with
                                           % the name you want, and uncomment
 % \begin{symbols}
 % \end{symbols}
 %                       % Use one of the two choices to add symbols text
 % \include{symbols}

 %% \renewcommand{\prefacename}{ } % If you want another Preface name, add
                                   % something else, and uncomment
 % \begin{preface}
 % \end{preface}
 %                       % Use one of the two choices to add preface text
 % \include{preface}

 %% \renewcommand{\acknowledgename}{ } % If you want another Acknowledgement name
                                       % add something else, and uncomment
 % \begin{acknowledge}
 % \end{acknowledge}
 %                       % Use one of the two choices to add acknowledge text
 % \include{acknowledgement}

\mainmatter
 % Place the text body here.
 \input{./hr/hr.tex}
 \input{./mnls/mnls}
 \chapter{Numerics}
\appendix
\chapter{}
\input{./mnls/mnls-appen.tex}

 % If you have appendices, add them here.
 % Begin each one with \chapter{title} as before- the \appendix command takes
 % care of renaming chapter headings and creates a new page in the Table of
 % Contents for them.
 % \include{appendix-one}

\backmatter              % Place for bibliography and index

%\bibliographystyle{amsplain}  % Use the ``nddiss2e'' biblio-style
%\bibliography{/Users/davidkarapetyan/math/bib-files/references.bib}           % input the bib-database file name
% \bib, bibdiv, biblist are defined by the amsrefs package.
\begin{bibdiv}
\begin{biblist}[\normalsize]

\bib{Benjamin_1972_Model-equations}{article}{
      author={Benjamin, T.~B.},
      author={Bona, J.~L.},
      author={Mahony, J.~J.},
       title={Model equations for long waves in nonlinear dispersive systems},
        date={1972},
        ISSN={0080-4614},
     journal={Philos. Trans. Roy. Soc. London Ser. A},
      volume={272},
      number={1220},
       pages={47\ndash 78},
}

\bib{Bressan_2007_Global-conserva}{article}{
      author={Bressan, Alberto},
      author={Constantin, Adrian},
       title={Global conservative solutions of the {C}amassa-{H}olm equation},
        date={2007},
        ISSN={0003-9527},
     journal={Arch. Ration. Mech. Anal.},
      volume={183},
      number={2},
       pages={215\ndash 239},
}

\bib{Bendahmane_2006_Hsp-1-perturbat}{article}{
      author={Bendahmane, Mostafa},
      author={Coclite, Giuseppe~Maria},
      author={Karlsen, Kenneth~H.},
       title={{$H\sp 1$}-perturbations of smooth solutions for a weakly
  dissipative hyperelastic-rod wave equation},
        date={2006},
        ISSN={1660-5446},
     journal={Mediterr. J. Math.},
      volume={3},
      number={3-4},
       pages={419\ndash 432},
}

\bib{Benjamin_1972_The-stability-o}{article}{
      author={Benjamin, T.~B.},
       title={The stability of solitary waves},
        date={1972},
        ISSN={0962-8444},
     journal={Proc. Roy. Soc. (London) Ser. A},
      volume={328},
       pages={153\ndash 183},
}

\bib{Burq_Gerad_Tzvetkov-An-instability-}{article}{
      author={Burq, N.},
      author={G{{\'e}}rad, P.},
      author={Tzvetkov, N.},
       title={An instability property of the nonlinear {S}chr{\"o}dinger
  equation on {$S^d$}},
        date={2002},
        ISSN={1073-2780},
     journal={Math. Res. Lett.},
      volume={9},
      number={2-3},
       pages={323\ndash 335},
}

\bib{Bona_2009_Sharp-well-pose}{article}{
      author={Bona, Jerry~L.},
      author={Tzvetkov, Nikolay},
       title={Sharp well-posedness results for the {BBM} equation},
        date={2009},
        ISSN={1078-0947},
     journal={Discrete Contin. Dyn. Syst.},
      volume={23},
      number={4},
       pages={1241\ndash 1252},
         url={http://dx.doi.org/10.3934/dcds.2009.23.1241},
}

\bib{Christ_2003_Asymptotics-fre}{article}{
      author={Christ, Michael},
      author={Colliander, James},
      author={Tao, Terrence},
       title={Asymptotics, frequency modulation, and low regularity
  ill-posedness for canonical defocusing equations},
        date={2003},
        ISSN={0002-9327},
     journal={Amer. J. Math.},
      volume={125},
      number={6},
       pages={1235\ndash 1293},
  url={http://muse.jhu.edu/journals/american_journal_of_mathematics/v125/125.6christ.pdf},
}

\bib{Coclite_2005_Global-weak-sol}{article}{
      author={Coclite, G.~M.},
      author={Holden, H.},
      author={Karlsen, K.~H.},
       title={Global weak solutions to a generalized hyperelastic-rod wave
  equation},
        date={2005},
        ISSN={0036-1410},
     journal={SIAM J. Math. Anal.},
      volume={37},
      number={4},
       pages={1044\ndash 1069 (electronic)},
}

\bib{Constantin_2000_Stability-of-a-}{article}{
      author={Constantin, Adrian},
      author={Strauss, Walter~A},
       title={Stability of a class of solitary waves in compressible elastic
  rods},
        date={2000},
     journal={Phys. Lett. A},
      volume={270},
      number={3-4},
       pages={140\ndash 148},
}

\bib{Dai_1998_Model-equations}{article}{
      author={Dai, H-H},
       title={Model equations for nonlinear dispersive waves in a compressible
  mooney-rivlin rod},
        date={1998},
     journal={Acta Mech.},
      volume={127},
      number={1-4},
       pages={193\ndash 207},
}

\bib{Dai_2000_Head-on-collisi}{article}{
      author={Dai, Hui-Hui},
      author={Dai, Shiqiang},
      author={Huo, Yi},
       title={Head-on collision between two solitary waves in a compressible
  mooney-rivlin elastic rod},
        date={2000},
     journal={Wave Motion},
      volume={32},
      number={2},
       pages={93\ndash 111},
}

\bib{Dai_2000_Solitary-shock-}{article}{
      author={Dai, Hui-Hui},
      author={Huo, Yi},
       title={Solitary shock waves and other travelling waves in a general
  compressible hyperelastic rod},
        date={2000},
     journal={R. Soc. Lond. Proc. Ser. A Math. Phys. Eng. Sci.},
      volume={456},
      number={1994},
       pages={331\ndash 363},
}

\bib{Dieudonne_1969_Foundations-of-}{book}{
      author={Dieudonn{{\'e}}, J.},
       title={Foundations of modern analysis},
   publisher={Academic Press},
     address={New York},
        date={1969},
        note={Enlarged and corrected printing, Pure and Applied Mathematics,
  Vol. 10-I},
}

\bib{Folland_1999_Real-analysis}{book}{
      author={Folland, Gerald~B.},
       title={Real analysis},
     edition={Second},
      series={Pure and Applied Mathematics (New York)},
   publisher={John Wiley \& Sons Inc.},
     address={New York},
        date={1999},
        ISBN={0-471-31716-0},
        note={Modern techniques and their applications, A Wiley-Interscience
  Publication},
}

\bib{Himonas:2009fk}{article}{
      author={Himonas, A.~Alexandrou},
      author={Kenig, Carlos},
       title={Non-uniform dependence on initial data for the {CH} equation on
  the line},
        date={2009},
        ISSN={0893-4983},
     journal={Differential Integral Equations},
      volume={22},
      number={3-4},
       pages={201\ndash 224},
}

\bib{Himonas_2009_Non-uniform-dep-per}{article}{
      author={Himonas, Alex},
      author={Kenig, Carlos~E.},
      author={Misiolek, G.},
       title={Non-uniform dependence for the periodic ch equation.},
        date={2009},
     journal={To appear in Communications in Partial Differential Equations},
}

\bib{Himonas-Misiolek-2001-A-priori-estimates-for-Schrodinger}{article}{
      author={Himonas, A.~Alexandrou},
      author={Misiolek, Gerard},
       title={A priori estimates for {S}chr{\"o}dinger type multipliers},
        date={2001},
        ISSN={0019-2082},
     journal={Illinois J. Math.},
      volume={45},
      number={2},
       pages={631\ndash 640},
}

\bib{Himonas_2001_The-Cauchy-prob}{article}{
      author={Himonas, Alex},
      author={Misiolek, Gerard},
       title={The {C}auchy problem for an integrable shallow-water equation},
        date={2001},
        ISSN={0893-4983},
     journal={Differential Integral Equations},
      volume={14},
      number={7},
       pages={821\ndash 831},
}

\bib{Himonas:2005kx}{article}{
      author={Himonas, A.~Alexandrou},
      author={Misiolek, Gerard},
       title={High-frequency smooth solutions and well-posedness of the
  {C}amassa-{H}olm equation},
        date={2005},
        ISSN={1073-7928},
     journal={Int. Math. Res. Not.},
      number={51},
       pages={3135\ndash 3151},
         url={http://dx.doi.org/10.1155/IMRN.2005.3135},
}

\bib{Himonas_2009_Non-uniform-dep-euler}{article}{
      author={Himonas, Alex},
      author={Misiolek, Gerard},
       title={Non-uniform dependence on initial data of solutions to the euler
  equations of hydrodynamics},
        date={2009, to appear},
     journal={Communications in Mathematical Physics},
}

\bib{Himonas_2007_Non-uniform-con}{article}{
      author={Himonas, Alex},
      author={Misiolek, Gerard},
      author={Ponce, Gustavo},
       title={Non-uniform continuity in {$H\sp 1$} of the solution map of the
  ch equation},
        date={2007},
     journal={Asian J. Math.},
      volume={11},
      number={1},
       pages={141\ndash 150},
}

\bib{Holden_2007_Global-conserva}{article}{
      author={Holden, Helge},
      author={Raynaud, Xavier},
       title={Global conservative solutions of the generalized hyperelastic-rod
  wave equation},
        date={2007},
     journal={J. Differential Equations},
      volume={233},
      number={2},
       pages={448\ndash 484},
}

\bib{Kato_1975_Quasi-linear-eq}{incollection}{
      author={Kato, Tosio},
       title={Quasi-linear equations of evolution, with applications to partial
  differential equations},
        date={1975},
   booktitle={Spectral theory and differential equations ({P}roc. {S}ympos.,
  {D}undee, 1974; dedicated to {K}onrad {J}{\"o}rgens)},
   publisher={Springer},
     address={Berlin},
       pages={25\ndash 70. Lecture Notes in Math., Vol. 448},
}

\bib{Kato_1988_Commutator-esti}{article}{
      author={Kato, Tosio},
      author={Ponce, Gustavo},
       title={Commutator estimates and the {E}uler and {N}avier-{S}tokes
  equations},
        date={1988},
        ISSN={0010-3640},
     journal={Comm. Pure Appl. Math.},
      volume={41},
      number={7},
       pages={891\ndash 907},
}

\bib{Kenig_2001_On-the-ill-pose}{article}{
      author={Kenig, Carlos~E.},
      author={Ponce, Gustavo},
      author={Vega, Luis},
       title={On the ill-posedness of some canonical dispersive equations},
        date={2001},
        ISSN={0012-7094},
     journal={Duke Math. J.},
      volume={106},
      number={3},
       pages={617\ndash 633},
         url={http://dx.doi.org/10.1215/S0012-7094-01-10638-8},
}

\bib{Koch_2005_Nonlinear-wave-}{article}{
      author={Koch, H.},
      author={Tzvetkov, N.},
       title={Nonlinear wave interactions for the {B}enjamin-{O}no equation},
        date={2005},
        ISSN={1073-7928},
     journal={Int. Math. Res. Not.},
      number={30},
       pages={1833\ndash 1847},
}

\bib{Lenells_2006_Traveling-waves}{article}{
      author={Lenells, Jonatan},
       title={Traveling waves in compressible elastic rods},
        date={2006},
        ISSN={1531-3492},
     journal={Discrete Contin. Dyn. Syst. Ser. B},
      volume={6},
      number={1},
       pages={151\ndash 167 (electronic)},
}

\bib{Li_2000_Well-posedness-}{article}{
      author={Li, Yi~A},
      author={Olver, Peter~J},
       title={Well-posedness and blow-up solutions for an integrable
  nonlinearly dispersive model wave equation},
        date={2000},
     journal={J. Differential Equations},
      volume={162},
      number={1},
       pages={27\ndash 63},
}

\bib{Mustafa_2007_Global-conserva}{article}{
      author={Mustafa, Octavian~G.},
       title={Global conservative solutions of the hyperelastic rod equation},
        date={2007},
        ISSN={1073-7928},
     journal={Int. Math. Res. Not. IMRN},
      number={13},
       pages={Art. ID rnm040, 26},
}

\bib{Olson_2006_Non-uniform-dep}{article}{
      author={Olson, Erika},
       title={Non-uniform dependence on initial data for a family of non-linear
  evolution equations},
        date={2006},
     journal={Differential Integral Equations},
      volume={19},
      number={10},
       pages={1081\ndash 1102},
}

\bib{Rodriguez-Blanco_2001_On-the-Cauchy-p}{article}{
      author={Rodr{\'{\i}}guez-Blanco, Guillermo},
       title={On the {C}auchy problem for the {C}amassa-{H}olm equation},
        date={2001},
        ISSN={0362-546X},
     journal={Nonlinear Anal.},
      volume={46},
      number={3, Ser. A: Theory Methods},
       pages={309\ndash 327},
}

\bib{Taylor_1991_Pseudodifferent}{book}{
      author={Taylor, Michael~E.},
       title={Pseudodifferential operators and nonlinear {PDE}},
      series={Progress in Mathematics},
   publisher={Birkh{\"a}user Boston Inc.},
     address={Boston, MA},
        date={1991},
      volume={100},
        ISBN={0-8176-3595-5},
}

\bib{Yin_2003_On-the-Cauchy-p}{article}{
      author={Yin, Zhaoyang},
       title={On the cauchy problem for a nonlinearly dispersive wave
  equation},
        date={2003},
     journal={J. Nonlinear Math. Phys.},
      volume={10},
      number={1},
       pages={10\ndash 15},
}

\bib{Zhou_2005_Local-well-pose}{article}{
      author={Zhou, Yong},
       title={Local well-posedness and blow-up criteria of solutions for a rod
  equation},
        date={2005},
     journal={Math. Nachr.},
      volume={278},
      number={14},
       pages={1726\ndash 1739},
}

\end{biblist}
\end{bibdiv}

\end{document}

%%
\endinput
%%
