\documentclass[12pt]{letter}
\usepackage[top=0.3cm,bottom=0.3cm]{geometry}
\renewcommand{\baselinestretch}{1.1} %increases vert spacing of text
\synctex=1
\name{David Karapetyan}
\signature{\vspace{-0.5cm}David Karapetyan}
%\longindentation=0pt
\date{\vspace{0.5cm}\flushleft}
\begin{document}

\begin{letter}{Global Recruiting \\
Citadel LLC \\
131 South Dearborn Street  \\
Chicago, IL 60603 USA 
}
\begin{center}
{\bf {\Large David Karapetyan}}
\end{center}

\begin{center}
{817 Hylan Hall, University of Rochester, NY 14607  \\ 
202-460-5173 \\  david.karapetyan@gmail.com
}
\end{center}
\hrule

\opening{Dear Members of the Hiring Committee:\\}
%
%
I wish to apply for positions in quantitative analysis and quantitative
trading at Citadel. I have singled Citadel out amongst hedge funds due to its status as the top options market maker in the Midwest, and as one of the top equity and options market makers in the world. I am also intrigued by its demanding culture, filtering those out who are dedicated and ambitious from those who are not. Having spent the past five years studying at Notre Dame for a Ph.D. in mathematics, I have been under immense pressure. What has kept me going is the desire to one day rise to the top, so as to give back to all those who have been supportive to me, and to make them proud. I feel that Citadel would be the ideal location to begin realizing my ambitions, and that the company would likewise benefit from my work ethic, skill set, and willpower if they were willing to bring me on board. 

I am currently researching \textbf{partial differential equations}, and in particular nonlinear evolution equations as a Visiting Assistant Professor at the University of Rochester. I received my Ph.D. in mathematics on May, 2012 from the University of Notre Dame. My
background in mathematics, and in particular my experience
\textbf{programming} numerical algorithms in \textbf{C++} and \textbf{MATLAB}
to aid my research, have given me the tools needed to build a career at Citadel.

In addition to my work at the University of Rocheser and at Notre Dame, I have alsoworked in Washington D.C. as a research
associate for both the Institute for Defense Analyses and the Battelle Memorial
Institute. My numerical and consulting experience at these two think tanks are
detailed in my resume. 

I am passionate about quantitative analysis in the financial sector due to its reliance on high level mathematics and programming to model macroeconomic phenomena. I am also passionate about the trading profession because of its blistering pace, and heavy use of mathematics and programming. 
If you have any questions, please do not hesitate to ask. It would be a
pleasure to interview with you, and I hope to hear from you soon. Thank you for
your time and consideration. 

\closing{Sincerely,}


\end{letter}

\end{document}
