\documentclass[12pt]{letter}
\usepackage[top=0.3cm,bottom=0.3cm]{geometry}
\renewcommand{\baselinestretch}{1.1} %increases vert spacing of text
\synctex=1
\name{David Karapetyan}
\signature{\vspace{-0.5cm}David Karapetyan}
%\longindentation=0pt
\date{\vspace{0.5cm}\flushleft}
\begin{document}

\begin{letter}{}
\begin{center}
{\bf {\Large David Karapetyan}}
\end{center}

\begin{center}
{819 Hylan Hall, University of Rochester, NY 14607  \\ 
202-460-5173 \\  david.karapetyan@gmail.com
}
\end{center}
\hrule

\opening{Dear Members of the Hiring Committee:\\}
%

%
I wish to apply for a position as a research analyst at the Center for Naval Analyses. I am currently researching partial differential equations, and in particular nonlinear
evolution equations as a Visiting Assistant Professor at the University of
Rochester. I received my Ph.D. in mathematics on May, 2012 from the University
of Notre Dame. While the academic world is wonderful, I miss the fast pace of
industry, and in particular how quickly good ideas are noticed and disseminated by colleagues and the firm itself. However, I also love mathematics, and dearly want to obtain
a position which is highly quantitative. Consequently, I feel work as a
research analyst at an established think tank would be a great fit for
me, as it would combine both preferences. However, I would overwhelmingly
prefer to work at CNA instead of any other think tank, due to the 
excellent word of mouth I received while at the Institute for Defense Analyses. I feel I could contribute immediately if hired, not only because of
my background in mathematics, but also because of my years of experience
programming numerical algorithms in C++, Ruby, and MATLAB to aid my research.

In addition to jobs held at the University of Rochester and at Notre Dame, I have
also worked in Washington D.C. as a research associate for both the Institute
for Defense Analyses and the Battelle Memorial Institute. My numerical and
consulting experience at these two think tanks are detailed in my resume. 

If you have any questions, please do not hesitate to ask. It would be a
pleasure to interview with you, and I hope to hear from you soon. Thank you for
your time and consideration. 

\closing{Sincerely,}


\end{letter}

\end{document}
