\documentclass[12pt,reqno]{amsbook}
%
%
%\usepackage[notcite, notref]{showkeys}
\usepackage[T1]{fontenc} %otherwise have font issues
\usepackage[utf8x]{inputenc}
\usepackage{lmodern} %this with above font packages give us all possible diacritics
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{appendix}
\usepackage{amssymb}
\usepackage{cancel}  %for cancelling terms explicity on pdf
\usepackage{yhmath}   %makes fourier transform look nicer, among other things
\usepackage{framed}  %for framing remarks, theorems, etc.
\usepackage{appendix}
\synctex=1
\usepackage{enumerate} %to change enumerate symbols
\usepackage[margin=2.5cm]{geometry}  %page layout
%\setcounter{tocdepth}{1} %must come before secnumdepth--else, pain
\setcounter{secnumdepth}{1} %number only sections, not subsections
%\usepackage[pdftex]{graphicx} %for importing pictures into latex--pdf compilation
\numberwithin{section}{chapter} 
\numberwithin{equation}{section}  %eliminate need for keeping track of counters
%\numberwithin{figure}{section}
%\setlength{\parindent}{0in} %no indentation of paragraphs after section title
%\setlength{\parskip}{0.1in} %ensure that blank source code lines generate space
% in amsbook class and others. Automatic for amsart
\renewcommand{\baselinestretch}{1.1} %increases vert spacing of text
%\renewcommand{\subsection}{\textbf} %temporary fix--subsection indents in
%amsbook, and want to disable it
%
\usepackage{hyperref}
\hypersetup{colorlinks=true,
linkcolor=blue,
citecolor=blue,
urlcolor=blue,
}
%\usepackage[alphabetic, initials, msc-links]{amsrefs} %for the bibliography; uses cite pkg. Must be loaded after hyperref, otherwise doesn't work properly (conflicts with cref in particular)
\usepackage{cleveref} %must be last loaded package to work properly
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{prop}[theorem]{Proposition}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{no}[theorem]{Notation}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{examp}{Example}[section]
\newtheorem {exercise}[theorem]{Exercise}
\newcommand{\ds}{\displaystyle}
\newcommand{\ts}{\textstyle}
\newcommand{\nin}{\noindent}
\newcommand{\rr}{\mathbb{R}}
\newcommand{\nn}{\mathbb{N}}
\newcommand{\zz}{\mathbb{Z}}
\newcommand{\cc}{\mathbb{C}}
\newcommand{\ci}{\mathbb{T}}
\newcommand{\zzdot}{\dot{\zz}}
\newcommand{\wh}{\widehat}
\newcommand{\p}{\partial}
\newcommand{\ee}{\varepsilon}
\newcommand{\vp}{\varphi}
\newcommand{\wt}{\widetilde}
%
%
\theoremstyle{remark}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{example}{Example}[section]
%
%
%
\newcommand{\uol}{u^\omega_\lambda}
\newcommand{\lbar}{\bar{l}}
\newcommand{\R}{\mathbb R}
\newcommand{\RR}{\mathcal R}
\newcommand{\al}{\alpha}
\newcommand{\ve}{q}
\newcommand{\tg}{{tan}}
\newcommand{\m}{q}
\newcommand{\N}{N}
\newcommand{\ta}{{\tilde{a}}}
\newcommand{\tb}{{\tilde{b}}}
\newcommand{\tc}{{\tilde{c}}}
\newcommand{\tS}{{\tilde S}}
\newcommand{\tP}{{\tilde P}}
\newcommand{\tu}{{\tilde{u}}}
\newcommand{\tw}{{\tilde{w}}}
\newcommand{\tA}{{\tilde{A}}}
\newcommand{\tX}{{\tilde{X}}}
\newcommand{\tphi}{{\tilde{\phi}}}
%\renewcommand{\qed}{\qquad \qedsymbol} %for proof env qed symbol
%\renewcommand \thepart{\Roman{part}} %change part labeling to Roman
%numeral--not needed for memoir
\renewcommand{\cref}{\Cref} %capitalize option for cleveref doesn't work on all
%computers


\begin{document}
\title{Notes}
\author{David Karapetyan}
%\address{Department of Mathematics, University of Notre Dame, Notre Dame, IN 46556}
%\email{dkarapet@nd.edu}

\date{}

\maketitle
\tableofcontents
\part{Strongly Dispersive Equations}
\include{mnls/mnls}
\include{nls-l4/nls-l4}
\include{dnls/dnls}
\include{kdv/kdv}
\include{knls/knls}
\include{mkdv/mkdv}
\include{nls-gevrey/nls-gevrey}
\part{Weakly Dispersive Equations}
\include{./hr/hr}
\include{./hr/hr_holder_cont}
\appendix

\include{ode-thm/ode-thm}
%
\providecommand{\bysame}{\leavevmode\hbox to3em{\hrulefill}\thinspace}
\providecommand{\MR}{\relax\ifhmode\unskip\space\fi MR }
% \MRhref is called by the amsart/book/proc definition of \MR.
\providecommand{\MRhref}[2]{%
  \href{http://www.ams.org/mathscinet-getitem?mr=#1}{#2}
}
\providecommand{\href}[2]{#2}
\begin{thebibliography}{HIKK10}

\bibitem[BBM72]{Benjamin_1972_Model-equations}
T.~B. Benjamin, J.~L. Bona, and J.~J. Mahony, \emph{{Model equations for long
  waves in nonlinear dispersive systems}}, Philos. Trans. Roy. Soc. London Ser.
  A \textbf{272} (1972), no.~1220, 47--78.

\bibitem[BC07]{Bressan_2007_Global-conserva}
A.~Bressan and A.~Constantin, \emph{{Global conservative solutions of the
  Camassa-Holm equation}}, Arch. Ration. Mech. Anal. \textbf{183} (2007),
  no.~2, 215--239.

\bibitem[BCK06]{Bendahmane:2006p1301}
M.~Bendahmane, G.~M. Coclite, and K.~H. Karlsen,
  \emph{$H^1$-perturbations of smooth solutions for a weakly dissipative
  hyperelastic-rod wave equation}, Mediterr. J. Math. \textbf{3} (2006),
  no.~3-4, 419--432.

\bibitem[Ben72]{Benjamin_1972_The-stability-o}
T.~B. Benjamin, \emph{{The stability of solitary waves}}, Proc. Roy. Soc.
  (London) Ser. A \textbf{328} (1972), 153--183.

\bibitem[BT09]{Bona_2009_Sharp-well-pose}
J.~L. Bona and N.~Tzvetkov, \emph{{Sharp well-posedness results for the BBM
  equation}}, Discrete Contin. Dyn. Syst. \textbf{23} (2009), no.~4,
  1241--1252.

\bibitem[CCT03]{Christ_2003_Asymptotics-fre}
M.~Christ, J.~Colliander, and T.~Tao, \emph{{Asymptotics, frequency modulation,
  and low regularity ill-posedness for canonical defocusing equations}}, Amer.
  J. Math. \textbf{125} (2003), no.~6, 1235--1293.

\bibitem[CH93]{Camassa-Holm-1993-An-integrable-shallow-water}
R.~Camassa and D.~D. Holm, \emph{{An integrable shallow water equation with
  peaked solitons}}, Phys. Rev. Lett. \textbf{71} (1993), no.~11, 1661--1664.

\bibitem[CHK05]{Coclite_2005_Global-weak-sol}
G.~M. Coclite, H.~Holden, and K.~H. Karlsen, \emph{{Global weak solutions to a
  generalized hyperelastic-rod wave equation}}, SIAM J. Math. Anal. \textbf{37}
  (2005), no.~4, 1044--1069 (electronic).

\bibitem[CL09]{Constantin-Lannes-2009-The-hydrodynamical-relevance-of-the-Camassa-Holm}
A.~Constantin and D.~Lannes, \emph{{The hydrodynamical relevance of the
  Camassa-Holm and Degasperis-Procesi equations}}, Arch. Ration. Mech. Anal.
  \textbf{192} (2009), no.~1, 165--186.

\bibitem[CLZ]{Chen:2011fk}
R.~M. Chen, Y.~Liu, and P.~Zhang, \emph{{The H{\"o}lder Continuity of the
  Solution Map to the {\$}b{\$}-family Equation in weak topology}}.

\bibitem[CS00a]{Constantin_2000_Stability-of-a-}
A.~Constantin and W.~A. Strauss, \emph{{Stability of a class of solitary waves
  in compressible elastic rods}}, Phys. Lett. A \textbf{270} (2000), no.~3-4,
  140--148.

\bibitem[CS00b]{Constantin_2000_Stability-of-pe}
\bysame, \emph{{Stability of peakons}}, Comm. Pure Appl. Math. \textbf{53}
  (2000), no.~5, 603--610.

\bibitem[Dai98]{Dai_1998_Model-equations}
H.-H. Dai, \emph{{Model equations for nonlinear dispersive waves in a
  compressible Mooney-Rivlin rod}}, Acta Mech. \textbf{127} (1998), no.~1-4,
  193--207.

\bibitem[DDH00]{Dai_2000_Head-on-collisi}
H.-H. Dai, S.~Dai, and Y.~Huo, \emph{{Head-on collision between two solitary
  waves in a compressible Mooney-Rivlin elastic rod}}, Wave Motion \textbf{32}
  (2000), no.~2, 93--111.

\bibitem[DH00]{Dai_2000_Solitary-shock-}
H.-H. Dai and Y.~Huo, \emph{{Solitary shock waves and other travelling waves in
  a general compressible hyperelastic rod}}, R. Soc. Lond. Proc. Ser. A Math.
  Phys. Eng. Sci. \textbf{456} (2000), no.~1994, 331--363.

\bibitem[Die69]{Dieudonne_1969_Foundations-of-}
J.~Dieudonn{\'e}, \emph{{Foundations of modern analysis}}, New York, 1969.

\bibitem[HIKK10]{Herr:2010p886}
S.~Herr, A.~D. Ionescu, C.~E. Kenig, and H.~Koch, \emph{{A para-differential
  renormalization technique for nonlinear dispersive equations}}, Comm. Partial
  Differential Equations \textbf{35} (2010), no.~10, 1827--1875.

\bibitem[HK09]{Himonas:2009fk}
A.~Himonas and C.~E. Kenig, \emph{{Non-uniform dependence on initial data for
  the CH equation on the line}}, Differential Integral Equations \textbf{22}
  (2009), no.~3-4, 201--224.

\bibitem[HKM10]{Himonas:2010p1187}
A.~Himonas, C.~Kenig, and G.~Misiolek, \emph{{Non-uniform dependence for the
  periodic CH equation}}, Comm. Partial Differential Equations \textbf{35}
  (2010), no.~6, 1145--1162.

\bibitem[HM01]{Himonas_2001_The-Cauchy-prob}
A.~Himonas and G.~Misiolek, \emph{{The Cauchy problem for an integrable
  shallow-water equation}}, Differential Integral Equations \textbf{14} (2001),
  no.~7, 821--831.

\bibitem[HM05]{Himonas:2005kx}
\bysame, \emph{{High-frequency smooth solutions and well-posedness of the
  Camassa-Holm equation}}, Int. Math. Res. Not. (2005), no.~51, 3135--3151.

\bibitem[HM09]{Himonas_2009_Non-uniform-dep-euler}
\bysame, \emph{{Non-uniform dependence on initial data of solutions to the
  Euler equations of hydrodynamics}}, Communications in Mathematical Physics
  (2009).

\bibitem[HMP07]{Himonas_2007_Non-uniform-con}
A.~Himonas, G.~Misiolek, and G.~Ponce, \emph{{Non-uniform continuity in {\$}H\^
  1{\$} of the solution map of the CH equation}}, Asian J. Math. \textbf{11}
  (2007), no.~1, 141--150.

\bibitem[HR07]{Holden_2007_Global-conserva}
H.~Holden and X.~Raynaud, \emph{{Global conservative solutions of the
  generalized hyperelastic-rod wave equation}}, J. Differential Equations
  \textbf{233} (2007), no.~2, 448--484.

\bibitem[iB01]{Rodriguez-Blanco_2001_On-the-Cauchy-p}
G.~R. iguez Blanco, \emph{{On the Cauchy problem for the Camassa-Holm
  equation}}, Nonlinear Anal. \textbf{46} (2001), no.~3, Ser. A: Theory
  Methods, 309--327.

\bibitem[Kar10]{Karapetyan:2010fk}
D.~Karapetyan, \emph{{Non-uniform dependence and well-posedness for the
  hyperelastic rod equation}}, J. Differential Equations \textbf{249} (2010),
  no.~4, 796--826.

\bibitem[Kat75]{Kato_1975_Quasi-linear-eq}
T.~Kato, \emph{{Quasi-linear equations of evolution, with applications to
  partial differential equations}}, 1975, pp.~25--70. Lecture Notes in Math.,
  Vol. 448.

\bibitem[KPV01]{Kenig_2001_On-the-ill-pose}
C.~E. Kenig, G.~Ponce, and L.~Vega, \emph{{On the ill-posedness of some
  canonical dispersive equations}}, Duke Math. J. \textbf{106} (2001), no.~3,
  617--633.

\bibitem[KT05]{Koch_2005_Nonlinear-wave-}
H.~Koch and N.~Tzvetkov, \emph{{Nonlinear wave interactions for the
  Benjamin-Ono equation}}, Int. Math. Res. Not. (2005), no.~30, 1833--1847.

\bibitem[Len06]{Lenells_2006_Traveling-waves}
J.~Lenells, \emph{{Traveling waves in compressible elastic rods}}, Discrete
  Contin. Dyn. Syst. Ser. B \textbf{6} (2006), no.~1, 151--167 (electronic).

\bibitem[LO00]{Li_2000_Well-posedness-}
Y.~A. Li and P.~J. Olver, \emph{{Well-posedness and blow-up solutions for an
  integrable nonlinearly dispersive model wave equation}}, J. Differential
  Equations \textbf{162} (2000), no.~1, 27--63.

\bibitem[Mol04]{Molinet_2004_On-well-posedne}
L.~Molinet, \emph{{On well-posedness results for Camassa-Holm equation on the
  line: a survey}}, J. Nonlinear Math. Phys. \textbf{11} (2004), no.~4,
  521--533.

\bibitem[Mus07]{Mustafa_2007_Global-conserva}
O.~G. Mustafa, \emph{{Global conservative solutions of the hyperelastic rod
  equation}}, Int. Math. Res. Not. IMRN (2007), no.~13, Art. ID rnm040, 26.

\bibitem[Ols06]{Olson_2006_Non-uniform-dep}
E.~Olson, \emph{{Non-uniform dependence on initial data for a family of
  non-linear evolution equations}}, Differential Integral Equations \textbf{19}
  (2006), no.~10, 1081--1102.

\bibitem[Tao04]{Tao:2004ck}
T.~Tao, \emph{Global well-posedness of the Benjamin-Ono equation in
  $H^1(\bf R)$}, J. Hyperbolic Differ. Equ. \textbf{1} (2004), no.~1,
  27--49.

\bibitem[Tay91]{Taylor_1991_Pseudodifferent}
M.~E. Taylor, \emph{{Pseudodifferential operators and nonlinear PDE}}, Boston,
  MA, 1991.

\bibitem[Tay95]{Taylor:1995kx}
\bysame, \emph{{Partial differential equations I, Basic theory}}, 1995.

\bibitem[Yin03]{Yin_2003_On-the-Cauchy-p}
Z.~Yin, \emph{{On the Cauchy problem for a nonlinearly dispersive wave
  equation}}, J. Nonlinear Math. Phys. \textbf{10} (2003), no.~1, 10--15.

\bibitem[Zho05]{Zhou_2005_Local-well-pose}
Y.~Zhou, \emph{{Local well-posedness and blow-up criteria of solutions for a
  rod equation}}, Math. Nachr. \textbf{278} (2005), no.~14, 1726--1739.

\end{thebibliography}
%
%\bibliographystyle{amsalpha-custom}
%\bibliography{/Users/davidkarapetyan/math/bib-files/references-papers}
%
%If want reference in normal size, do \begin{biblist}[\normalsize]
\end{document}
