 \documentclass[12pt]{amsart}
\usepackage{latest}
%\usepackage{pdfsync}
\usepackage[pdftex]{epsfig}
\usepackage{epstopdf}
\usepackage{enumerate}
\usepackage{calc,ifthen}
\usepackage{graphicx}
\newcommand{\m}{\hspace{1em}}
\synctex=1

\synctex=1

%%%%%

\def \sm {\smallskip}
\def\diff{{d\over{dx}}\,}
\def\ds{\displaystyle}
\def\headline{\vskip.25in \noindent}
\def\scr{\scriptstyle}
\def \hs {~~~~~~}
\def \hh {~~~}
\def\medno{\medskip \noindent}
\def\bigno{\bigskip \noindent}
\def\smno{\smallskip \noindent}
\def\smallno{\smallskip \noindent}
\def\D{\mathrm{d}}

%%%%


\begin{document}
%:%% prelim, final, webpage
\runType[final]


%: \begin{answersheetmatter}
\begin{answersheetmatter}[final]
\whichCourse[Math. 10260]
\whichExam[Final Exam]
\dateOfExam[5/6/2010]
\lengthOfTimeForExam[two hours]

\begin{multiplechoiceStyle}[dotted]% [dotted] or [blank] missing=blank
\breakAnswersAt{16} % first even past a half
%: permutations
\ll 1 23415
\ll 2 12543
\ll 3 35421
\ll 4 43512
\ll 5 13425
\ll 6 21435
\ll 7 32145
\ll 8 15342
\ll 9 35241
\ll 10 43521
\ll 11 12534
\ll 12 51243
\ll 13 42513
\ll 14 32514
\ll 15 42153
\ll 16 12543
\ll 17 23541
\ll 18 35421
\ll 19 25413
\ll 20 53241
\ll 21 52134
\ll 22 25134
\ll 23 13425
\ll 24 31254
\ll 25 52134
\ll 26 23541
\ll 27 51243
\ll 28 35421
\ll 29 53241
\ll 30 42153
\ll 31 43521
\end{multiplechoiceStyle}
\end{answersheetmatter}



\makeanswersheet[]
%: begin{exam}
\begin{exam}

\multiplechoiceStart[5 pts.]

% 1  
\begin{problem}
The marginal cost in dollars,  for producing $x$
units of a certain product is given by $\,\ds MC(x)=0.2x+20$. The
cost for producing 10 units is $\$300$. Find the cost for
producing 20 units.
%
\begin{answers}{1}
$\;\$530$ \\
$\;\$550$ \\
$\;\$540$ \\
$\;\$520$ \\
$\;\$510$ \\
\end{answers}
\end{problem}


%   2   
\begin{problem}
A company's marginal  profit per week is given by $MP(x)=-0.2x+50$, $10\le
x\le 30$. Find the total change in its profit when its production
level is raised from 10 to 20 units  per week.
 %
\begin{answers}{1}
$\;\$470$ \\
$\;\$530$ \\
$\;\$550$ \\
$\;\$490$ \\
$\;\$510$ \\
\end{answers}

\end{problem}


%  3 
\begin{problem}
Compute the area of the region enclosed by the
curves of $y=x^2$ and $y=x$.
%
\begin{answers}{1}
$\;1/6$ \\
$\;-1/6$\\
$\;1/3$ \\
$\;-1/3$\\
$\;2/3$ \\
\end{answers}

\end{problem}





% 4  
\begin{problem}
A certain item has supply function
$S(q) = 4q+1$ and demand function
$D(q) = (5-q)^2$ for $0 \le q \le 5$.
Find the equilibrium quantity $q_e$.
%
\begin{answers}1
$2$ \\
$0$ \\
$4$ \\
$9$ \\
$5$ \\
\end{answers}
\end{problem}



%  5 
\begin{problem}
Adriana opens a savings account with an initial deposit of $\$$1000.
The annual rate is 6$\%$ compounded continuously. Adriana pledges that
each year she'll continue to deposit money into the account 
{\bf continuously} at a rate
of  $\$1500$ per year. Which of the following initial value problems describes
her account's balance $M$ as a function of time $t$?
%
\begin{answers}1
$\frac{\D M}{\D t} = 0.06M+1500,\ M(0)=1000$ \\
$\frac{\D M}{\D t}=Me^{0.06t}+ 1500,\ M(0) =1000$ \\
$\frac{\D M}{\D t} = 0.06M-1500,\ M(0)=1000$ \\
$\frac{\D M}{\D t} = 0.06M+1000,\ M(0)=1500$ \\
$\frac{\D M}{\D t}=Me^{0.06t}+1500 e^{0.09t},\ M(0)=1000$ \\
\end{answers}
\end{problem}





%  6 
\begin{problem}
Which one of the following differential equations is NOT separable?
%
\begin{answers}1
$\frac{\D y}{\D t}=t+y$ \\
$\frac{\D y}{\D t}=e^t e^y$ \\
$\frac{\D y}{\D t}=y t$ \\
$\frac{\D y}{\D t}=1$ \\
$\frac{\D y}{\D t}=t^3$ \\
\end{answers}
\end{problem}





%   7 
\begin{problem}
You deposit money continuously into an account at a rate of $1,000$ dollars per
year. If the account yields $7\%$ interest, compounded continuously, how much
will be in the account after $10$ years? Round your answer to the nearest
dollar. 
%
\begin{answers}{1}
$14,482$\\  
$13,014$\\  
$29,164$\\ 
$17,192$\\
$10,138$ \\
\end{answers}

%
\end{problem}




%  8  
\begin{problem}
Which of the following improper integrals DIVERGE \@?
\\
\\
\medno 
$\mbox{(I)}\ \int_0^\infty e^{-1000 x}\D x \qquad \mbox{(II)}  
\int_0^1 \frac{1}{\sqrt{x}}\D  x \quad \mbox{(III)}  
\int_0^{\infty} e^{0.00001 x}\D  x 
\qquad \mbox{(IV)}  
\int_1^\infty \frac{1}{\sqrt{x}}\D  x \quad \qquad $
%
\begin{answers}{1}
(III) and (IV) \\
(I) and (IV) \\
(II) and (IV) \\
(I) and (III) \\
(II) and (III)\\
\end{answers}
\end{problem}





% 9 
\begin{problem}
Find the equation of the tangent plane to the graph of
the function $f(x, y) = xy - ye^x$  at the point 
where $x=0$ and $y=1$.  
%
\begin{answers}1
$z=y$\\
$z=-y$ \\
$z=y+1$\\
$z=x+y$\\
$z=y-1$\\
\end{answers}
\end{problem}








% 10 
\begin{problem}
Consider a function $f(x,y)$ of two variables.  Suppose that
$f(1,2) = 5$, 
$\frac{\partial f}{\partial x}(1,2) = -4$, and
$\frac{\partial f}{\partial y}(1,2) = 10$.  Use linear approximation
to estimate $f(1.1, 1.9)$.
\begin{answers}{1}
$3.6$ \\
$21$ \\
$19.6$  \\
$-1.4$ \\
$1.4$  \\
\end{answers}
\end{problem}

%11
\begin{problem}
What can you say about the behaviour of $ f(x,y)=x^3-0.5y^2-3x+2y+1$ at its 
critical point(s)? 
\begin{answers}{1}
$f(x, y)$ has a saddle point at $(1, 2)$ and a local maximum at $(-1, 2)$ \\
$f(x, y)$ has a local  maximum at $(1, 2)$ and a local minimum at $(-1, 2)$ \\
$f(x, y)$ has a local  maximum at $(1, 2)$ and a saddle point at $(-1, 2)$ \\
$f(x, y)$ has a local  minimum at $(1, 2)$ and a local maximum at $(-1, 2)$ \\
$f(x, y)$ has a saddle point at $(1, 2)$ and a local minimum at $(-1, 2)$ \\
\end{answers}
\end{problem}


% 12
\begin{problem}
If you want to find the least squares line of the form 
$y = ax + b$ for the  data  $(1, 2)$, $(2, 5)$, and $(5, 1)$,
which of the following error functions would you need to minimize in order to determine 
the values of $a$ and $b$?
%
\begin{answers}{1}
$E(a, b) = (a + b - 2)^2 + (2a + b - 5)^2 + (5a + b - 1)^2$ \\
$E(a, b) = (a + 2b)^2 + (2a + 5b)^2 + (5a + b)^2$ \\
$E(a, b) = (a + b - 2) + (2a + b - 5) + (5a + b - 1)$ \\
$E(a, b) = (a + b )^2 + (2a + b - 5)^2 + (5a + b - 1)^2$ \\
$E(a, b) = 2(a + b - 2) + 2(2a + b - 5) + 2(5a + b - 1)$ \\
\end{answers}
\end{problem}
%
%  13  
\begin{problem}
A manufacturing company's production is given by 
$\ds f(x,y)=4x^{\frac{1}{4}}y^{\frac{3}{4}}$ 
where $x$ is the units of capital and $y$
is the units of labor.  Suppose that the company's total budget is $\$1,200,000$
and that each unit of capital costs $\$60$ and each unit of labor costs $\$20$.
 Find the combination of $x$ and $y$ that will maximize the production
$f(x,y)$.
%
\begin{answers}{1}
$x=$5,000 and $y$=45,000\\
$x=$1,000 and $y$=60,000\\
$x=$20,000 and $y$=0\\
$x=$5,000 and $y$=40,000\\
$x=$0 and $y$=60,000  \\
\end{answers}
\end{problem}





% 14 
\begin{problem}
Given the differential equation $\ds \dfrac{dy}{dt} = 2ty$ with initial value
$y(0)=1$, estimate $y(0.2)$ using Euler's method with $\Delta t=0.1$.
\begin{answers}{3}
$1.02$ \\
$3.6$\\
$1.14$ \\
$-1.02$ \\
$1.23$ \\
\end{answers}

\end{problem}






% 15 
\begin{problem}
Assume that a certain population is modeled by the initial value problem
$$\frac{dp}{dt}=-5\ln (\frac{p}{250}),\quad p(0)=180,$$
where $p$ is in thousands and $t$ is in years.
Compute the limiting value of the population as $t\to\infty$.
(Hint: Find equilibrium solution and determine its stability.)
%
\begin{answers}{1}
$250$ \\
$180$\\
$-5$ \\
$5$ \\
$-250$ \\
\end{answers}

\end{problem}









%  16 
\begin{problem}
Suppose $\frac{dy}{dt}=1-e^{y-8}$.  Which one of
the following is true?
%
%
\begin{answers}{1}
$y=8$ is a stable equilibrium solution. \\
$y=8$ is an unstable equilibrium solution. \\
$y=8$ is an equilibrium solution that is neither stable nor
unstable. \\
The solution to the differential equation is decreasing when
$y=5$. \\
The solution to the differential equation is increasing when
$y=9$. \\
\end{answers}
\end{problem}










%   17  
\begin{problem}
Given the following direction field \textbf{NEED FIGURE}, find the matching
differential equation:
% 
 \begin{answers}{1}
$\frac{dy}{dt}=y(y-2)$ \\
$\frac{dy}{dt}=1-e^{2-y}$ \\
$\frac{dy}{dt}=y(2-y)$ \\
$\frac{dy}{dt}=\ln(\frac 2y)$ \\
$\frac{dy}{dt}=ty$ \\
%\begin{minipage}[b]{2.5in}
% $\epsfxsize=2.5in\epsfbox{fig1_final_S04.eps}$
%\end{minipage}
\end{answers}
\end{problem}


%  18 
\begin{problem}
Compute the Taylor polynomial of degree $n=2$ of
$\ds f(x)=\dfrac{1}{x^2}$ about
$a=-1$.

\begin{answers}{1}
$ P_2(x)=1+2(x+1)+3(x+1)^2$\\
$ P_2(x)=1+2(x-1)+3(x-1)^2$ \\
$ P_2(x)=1+2(x+1)+6(x+1)^2$ \\
$ P_2(x)=1-2(x+1)+3(x+1)^2$\\
$ P_2(x)=1+2x+3x^2$\\
\end{answers}
\end{problem}



% 19  
\begin{problem}
If $y(t)$ solves the initial value problem
$$
\frac{dy}{dt}=t^3+5y,\quad y(0)=2,
$$
then compute its Taylor polynomial approximation of degree $n=2$ 
about $a=0$.
%
\begin{answers}{1}
$P_2(x)=2+10t+25t^2$ \\
$ P_2(x)=2+10t+50t^2$ \\
$ P_2(x)=2+50t+\frac{125}{2}t^2$ \\
$ P_2(x)=2+10t+\frac{5}{2}t^2$ \\
$ P_2(x)=10+5t$\\
\end{answers}
\end{problem}





% 20 
\begin{problem}
Find the Taylor series of $f(t)=\frac{8}{1-t}$
about $a=0$.
%
\begin{answers}{1}
$\sum_{k=0}^{\infty}8 t^k=8+8t+8t^2+\cdots$ \\
$\sum_{k=0}^{\infty}8 (-t)^k=8-8t+8t^2-\cdots$\\
$\sum_{k=0}^{\infty} t^k=1+t+t^2+\cdots$ \\
$\sum_{k=0}^{\infty}-8 t^k=-8-8t-8t^2-\cdots$\\
$\sum_{k=1}^{\infty}8 t^k=8t+8t^2+8t^3+\cdots$\\
\end{answers}
\end{problem}





% 21 
\begin{problem}
Assume that the probability of a successful landing of a
 Mars Rover by NASA is 0.9.  Find the probability that
{\bf both} of the next two Mars Rovers {\bf fail} to
land on Mars assuming that these missions are independent from
each other.

\begin{answers}{1}
$0.81$ \\
$0.01$ \\
$1.80$ \\
$0.20$ \\
$0.99$ \\
\end{answers}
\end{problem}








%  22  
\begin{problem}
Based on  statistical data, an auto insurance
company considers  that 20\% of the drivers are accident prone, and
there is a 0.4 probability that an accident prone driver will have an
accident within a three year period.   For drivers that are not prone to
accidents the corresponding probability is 0.1.  Find the probability
that a  policy holder is accident prone given that he has an accident
within the first three years.
 %
\begin{answers}1
0.5 \\
0.08 \\
0.2 \\
0.6 \\
2 \\
\end{answers}
\end{problem}







% 23
\begin{problem}
Complete the following table so that it
becomes the probability distribution 
of a random variable $X$.

\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
$x$ & 0 & 2 & 3 & 4 \\
\hline
$P(X = x)$ & $0.5$ & $0.2$ & $0.1$ &? \\
\hline
\end{tabular}
\end{center}
Which one of the following numbers is its expected value $E(X)$?
%
\begin{answers}{1}
$1.5$ \\
$0.25$\\
$1.0$ \\
$2.3$ \\
$2.5$ \\
\end{answers}
\end{problem}









%  24 
\begin{problem}
Suppose X is a continuous random variable whose range is the interval
\phantom{sp} [0, 4].
The probability density function $f(x)$ for X is pictured below \textbf{NEED
FIGURE}, where the area of the region over the interval [0, 2] is 0.3. Find the
probability that X is between 2 and 4.
 %
\begin{answers}{1}
$0.7$\\
$0.3$\\
$0.4$\\
$0.5$\\
$0.6$\\
%\begin{minipage}[b]{0.5in}
%$\epsfxsize=2.8in\epsfbox{fig2_S04.eps}$
%\end{minipage}
\end{answers}
\end{problem}


%  25 
\begin{problem}
 A study concluded that the waiting time (in minutes) to be helped at
the Department of Motor Vehicles has an exponential distribution with
$\lambda=0.02$ (that is, its probability density function is $f(x)=0.02
e^{-0.02x}$). What is the probability that you have to wait more than 50 minutes
the next time you visit this office? 
%
\begin{answers}{1}
$e^{-1}$ \\
$e$ \\
$0.02$ \\
$1$ \\
$\frac{1}{0.02}$ \\
\end{answers}
%
\end{problem}



%  26 
\begin{problem}
Consider the function $f(x) = cx^4$ on the interval $[-1,1]$, where
$c$ is some constant.  Find $c$ such that $f(x)$ is a probability
density function on $[-1,1]$.
%
\begin{answers}{1}
$\frac{5}{2}$ \\
$0$ \\
$\frac{2}{5}$ \\
$1$ \\
$5$\\
%
\end{answers}
\end{problem}



%   27 
\begin{problem}
A random variable $X$ has probability density function $f(x) = 3x^2$
on the interval $[0,1]$.  Compute the variance $\mbox{Var}(X)$.  
%
\begin{answers}{1}
$\frac{3}{80}$ \\
$\frac{4}{3}$ \\
$\frac{3}{5}$ \\
$\frac{3}{4}$ \\
$\frac{9}{16}$ \\
%
\end{answers}
\end{problem}


%  28 
\begin{problem}
Assume that the bus for O'Hare passes through 
its Notre Dame station exactly every two hours, and that you plan to go 
to the station at a random time.  
What is the probability that you have to wait more
than 30 minutes?
%
\begin{answers}{1}
0.75\\
0.25\\
0.65\\
0.15 \\
0.30\\
%
\end{answers}
\end{problem}



% 29 
\begin{problem}
John, a regular customer of the SubWay in Lafortune, recorded the 
following waiting times, in minutes, over the last 10 days he had lunch there: 
5, 8, 10, 12, 14, 16, 18, 20, 22, 25.  Being mathematically inclined, he
suspects that the waiting time is a random variable with an exponential
distribution.  What would be his best guess for the parameter $\lambda $?
%
\begin{answers}{1}
15	\\
$\frac{1}{15}$	\\
$\frac{1}{5}$ \\
$\frac{1}{3}$ \\
$\frac{1}{225}$\\
%
\end{answers}
\end{problem}




%  30 
\begin{problem}
Assume that the weekly profit, in dollars, of the Starbucks
coffee shop in Lafortune is normally distributed
with mean $\mu = 3000$ and standard 
deviation $\sigma = 500$.  What percentage of the
weeks will the profit be less than 3500?
You will need to use the following table for $ \Phi(x)$, the 
cumulative distribution function for
the standard normal distribution    
\[
\Phi(x) = \frac{1}{\sqrt{2\pi}}\int_{-\infty}^{x} e^{-\frac{1}{2}t^2} dt.
\]
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
\hline
$x$       & $0$   & $0.5$    & $1$      & $1.5$    & 
            $2$      & $2.5$ \\ \hline
$\Phi(x)$  & $0.5$ & $0.6915$ & $0.8413$ & $0.9332$ &
            $0.9772$ & $0.9938$ \\
\hline
\end{tabular}
\end{center}
%
\begin{answers}{1}
84.13  \%  \\
50.00 \% \\
69.15\% \\
97.72 \% \\
93.32 \% \\
%
\end{answers}



\end{problem}















\end{exam}

\makemarkedanswersheet
\end{document}
