%
\documentclass[12pt,reqno]{amsart}
\usepackage{amssymb}
\usepackage{cancel}  %for cancelling terms explicity on pdf
\usepackage{yhmath}   %makes fourier transform look nicer, among other things
%\usepackage{showkeys}
\usepackage{framed}  %for framing remarks, theorems, etc.
%\usepackage{showkeys}  %shows source equation labels on the pdf
\usepackage[margin=3cm]{geometry}  %page layout
%\usepackage[pdftex]{graphicx} %for importing pictures into latex--pdf compilation
\setcounter{secnumdepth}{1} %number only sections, not subsections
\usepackage{hyperref}
\hypersetup{colorlinks=true,
	linkcolor=blue,
	citecolor=blue,
	urlcolor=blue,
}
\usepackage[alphabetic, initials, msc-links]{amsrefs} %for the bibliography; uses cite pkg. Must be loaded after hyperref, otherwise doesn't work properly (conflicts with cref in particular)
\synctex=1
\numberwithin{equation}{section}  %eliminate need for keeping track of counters
\numberwithin{figure}{section}
\setlength{\parindent}{0in} %no indentation of paragraphs after section title
\renewcommand{\baselinestretch}{1.1} %increases vert spacing of text
%
%
\newcommand{\ds}{\displaystyle}
\newcommand{\ts}{\textstyle}
\newcommand{\nin}{\noindent}
\newcommand{\rr}{\mathbb{R}}
\newcommand{\nn}{\mathbb{N}}
\newcommand{\zz}{\mathbb{Z}}
\newcommand{\cc}{\mathbb{C}}
\newcommand{\ci}{\mathbb{T}}
\newcommand{\zzdot}{\dot{\zz}}
\newcommand{\wh}{\widehat}
\newcommand{\p}{\partial}
\newcommand{\ee}{\varepsilon}
\newcommand{\vp}{\varphi}
%
%
\theoremstyle{plain}  
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{claim}{Claim}
\newtheorem{conjecture}[subsection]{conjecture}
%
\theoremstyle{definition}
\newtheorem{definition}{Definition}
%
\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
%
\makeatletter \renewenvironment{proof}[1][\proofname] {\par\pushQED{\qed}\normalfont\topsep6\p@\@plus6\p@\relax\trivlist\item[\hskip\labelsep\bfseries#1\@addpunct{.}]\ignorespaces}{\popQED\endtrivlist\@endpefalse} \makeatother%
%makes proof environment bold instead of italic
%
%
\def\makeautorefname#1#2{\expandafter\def\csname#1autorefname\endcsname{#2}}
\makeautorefname{equation}{Equation}
\makeautorefname{footnote}{footnote}
\makeautorefname{item}{item}
\makeautorefname{figure}{Figure}
\makeautorefname{table}{Table}
\makeautorefname{part}{Part}
\makeautorefname{appendix}{Appendix}
\makeautorefname{chapter}{Chapter}
\makeautorefname{section}{Section}
\makeautorefname{subsection}{Section}
\makeautorefname{subsubsection}{Section}
\makeautorefname{paragraph}{Paragraph}
\makeautorefname{subparagraph}{Paragraph}
\makeautorefname{theorem}{Theorem}
\makeautorefname{theo}{Theorem}
\makeautorefname{thm}{Theorem}
\makeautorefname{addendum}{Addendum}
\makeautorefname{add}{Addendum}
\makeautorefname{maintheorem}{Main theorem}
\makeautorefname{corollary}{Corollary}
\makeautorefname{lemma}{Lemma}
\makeautorefname{sublemma}{Sublemma}
\makeautorefname{proposition}{Proposition}
\makeautorefname{property}{Property}
\makeautorefname{scholium}{Scholium}
\makeautorefname{step}{Step}
\makeautorefname{conjecture}{Conjecture}
\makeautorefname{question}{Question}
\makeautorefname{definition}{Definition}
\makeautorefname{notation}{Notation}
\makeautorefname{remark}{Remark}
\makeautorefname{remarks}{Remarks}
\makeautorefname{example}{Example}
\makeautorefname{algorithm}{Algorithm}
\makeautorefname{axiom}{Axiom}
\makeautorefname{case}{Case}
\makeautorefname{claim}{Claim}
\makeautorefname{assumption}{Assumption}
\makeautorefname{conclusion}{Conclusion}
\makeautorefname{condition}{Condition}
\makeautorefname{construction}{Construction}
\makeautorefname{criterion}{Criterion}
\makeautorefname{exercise}{Exercise}
\makeautorefname{problem}{Problem}
\makeautorefname{solution}{Solution}
\makeautorefname{summary}{Summary}
\makeautorefname{operation}{Operation}
\makeautorefname{observation}{Observation}
\makeautorefname{convention}{Convention}
\makeautorefname{warning}{Warning}
\makeautorefname{note}{Note}
\makeautorefname{fact}{Fact}
%
\begin{document}
\title{The Metric Space ODE Theorem}
\author{David Karapetyan}
\address{Department of Mathematics  \\
	University  of Notre Dame\\
		Notre Dame, IN 46556 }
		\date{\today}
		%
		\maketitle
		%
		%
		%
		%
		%
		%
%
%
\section{Introduction}
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%				Notation
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%


Our goal will be to prove the following.
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%				Existence Theorem
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\begin{theorem}[Metric Space ODE Theorem]
	\label{ode-thm}
  Let $(X,d)$ be a metric, $E \subset X$ open, $u_0 \in E$, and $(-a, a)$ an
	open interval in $\rr$. If $f: (-a, a) \times E \to X$ satisfies the
	inequality
	%
	%
	\begin{equation}
		\label{stronger-ode}
		\begin{split}
      d[f(t, x), f(t, y)] \le c d(x, y), \qquad \forall t \in (-a, a),
			\qquad \forall x, y \in E,
		\end{split}
	\end{equation}
	%
  then for sufficiently small $h > 0$ there exists a unique
	differentiable map $u: (-h, h) \to E$ such that for all $t \in (-h, h)$
	%
	%
	\begin{gather}
    \label{ode-thm-eq}
			u'(t) = f(t, u(t)),
			\\
      \label{ode-thm-init-data}
			u(0) = u_0.
	\end{gather}
\end{theorem}
%
%
Notice that \autoref{ode-thm} is a 
generalization of the following classical result.
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%				 Picard-Lindelof
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\begin{theorem}[Picard-Lindel\"{o}f]
	Let $f(t, x)$ be a continuous function on $(- a, a) \times (- b,
	b)$ such that
	%
	%
	\begin{equation*}
		\begin{split}
			| f(t, x) - f(t, y) | \le c| x - y |, \quad \forall t \in (-a, a),
			\quad \forall x,y \in (- b, b).
		\end{split}
	\end{equation*}
	%
	%
	Then for any $\xi \in (-b, b)$ there exists an interval $(-h, h)
	\subset (-a, a)$ such that the initial value problem
	%
	%
	\begin{gather}
			\frac{dx}{dt} = f(t, x(t)),
			\\
			x(0) = \xi 
	\end{gather}
	%
	%
	has a unique solution $x(t)$ for all $t \in (-h, h)$.
	%
	%
	\end{theorem}
To prove \autoref{ode-thm}, we will first define
integration over Banach space. (To extend the theory of integration
to arbitrary complete metric spaces, one need only replace norms with metrics in
the definitions. We leave this to the reader.) Using which we will use to
rewrite \eqref{ode-thm-eq} as an integral equation. A fixed point
argument will then complete the proof. These notes are heavily influenced by a
number of excellent books, among them Dieudonn{\'e}
\cite{Dieudonne_1969_Foundations-of-}, Yosida \cite{Yosida:1980fk},
Folland \cite{Folland_1999_Real-analysis}, Jost
\cite{Jost-1998-Postmodern-analysis}, Rudin \cite{Rudin:1976uq}, and Knapp
\cite{Knapp:2005rm}-\cite{Knapp:2005yg}.
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%				 Differentiaion in Banach Spaces
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%				 Integration in Banach Spaces
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\section{Integration in Banach Spaces}
\label{sec:int-banach}
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%				Definition of step functions
%
%
%
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%				Definition of step function
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\begin{definition}
	A mapping $f:[a,b] \to X$ is a \emph{step-function} if there exists a disjoint
	partitioning $\left\{ (t_{j}, t_{j+1}) \right\}$ of $[a,b]$ such that
	%
	%
	\begin{equation}
		\label{step-function}
		\begin{split}
			f(t)=\sum_{j=0}^{n-1} {\alpha_j} \chi_{(t_{j}, t_{j+1})}.
		\end{split}
	\end{equation}
	%
	%
\end{definition}
%
%
\begin{framed}
\begin{example}
	The map $f:[-1,1] \to L^2(\rr)$ given by 
	%
	%
	\begin{equation*}
		\begin{split}
			f(t) = 
			\begin{cases}
				 e^{-x^2},  \quad & -1 \le t\le0 \\
				 e^{-2x^2},  \quad & \phantom - 0 < t \le 1 \\
				 0,  \quad & \phantom - \text{otherwise}
			\end{cases}
		\end{split}
	\end{equation*}
	%
	%
	is a step-function.
	\end{example}
\end{framed}
%
%
\begin{definition}[Banach Space Integration for Step Functions]
	Let $X$ be a Banach space, $f: [a,b] \to
	X$ a step function as in \eqref{step-function}. 
	Then 
	%
	\begin{equation*}
		\begin{split}
      \int_a^b f(t) dt \doteq \sum_{j=0}^{n-1} \alpha_j (t_{j+1} - t_{j}).
    \end{split}
	\end{equation*}
	%
	%
%
\end{definition}
%
%
Note that this definition is independent of the partitioning we use for $f$, due
to the following lemma.
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%                Indpendence of Partioning
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\begin{lemma}
For step functions $f, g$, we have
%
%
\begin{equation*}
\begin{split}
  \int_{a}^{b} f(t) dt - \int_{a}^{b} g(t) dt = \int_{a}^{b}\left[ f(t) - g(t) \right]dt.
\end{split}
\end{equation*}
%
%
\label{lem:indep-part}
\end{lemma}
%
%
\begin{proof}
%
Let
%
\begin{equation*}
\begin{split}
  & f = \sum_{j=1}^{m}\alpha_{j} \chi_{(t_{j}, t_{j+1})}
  \\
  & g = \sum_{k =1}^{n}
  \beta_{k} \chi_{(s_{k}, s_{k+1})}
\end{split}
\end{equation*}
%
and assume without loss of generality that $n \ge m$. 
Then
%
%
\begin{equation*}
\begin{split}
  f(t) - g(t) = \sum_{p=1}^{m+n} \gamma_{p} \chi_{(y_{p}, y_{p+1})} 
\end{split}
\end{equation*}
%
%
where
\begin{equation*}
  \begin{split}
    \gamma_{p} \chi_{(y_{p}, y_{p+1}) } = 
    \begin{cases}
      \alpha_{p} \chi_{(t_{p}, t_{p+1})}
, \quad & 1 \le p \le m \\
-\beta_{p-m} \chi_{(s_{p-m}, s_{p-m+1})}, \quad & m < p \le m+n.
\end{cases}
\end{split}
\end{equation*}
Then
%
%
%
\begin{equation*}
\begin{split}
  \int_{a}^{b}\left[ f(t) - g(t) \right]dt
  & = \sum_{p=1}^{m+n}
  \gamma_{p}(t_{p+1} - t_{p})
  \\
  & = \sum_{p=1}^{m} \gamma_{p}(t_{p+1} - t_{p}) +
  \sum_{p=1}^{m+n}\gamma_{p}(t_{p+1} - t_{p})
  \\
  & = \sum_{p=1}^{m} \alpha_{p}(t_{p+1} - t_{p}) +
  \sum_{p=m+1}^{m+n}-\beta_{p-m}(s_{p-m+1} - s_{p-m})
  \\
  & = \sum_{j=1}^{m}\alpha_{j}(t_{j+1} - t_{j}) -
  \sum_{k=1}^{n}\beta_{k}(s_{k+1} - s_{k})
  \\
  & = \int_{a}^{b}f(t)dt - \int_{a}^{b} g(t) dt.
\end{split}
\end{equation*}
%
%
%
%
\end{proof}
%
We are now interested in extending integration to a larger class of functions. We will need the
following. %
%
\begin{lemma}
	\label{lem:dense}
	Let $X$ be a Banach space, and
	suppose the function $f:[a,b] \to X$ is continuous . Then
	there exists a sequence of step functions $\left\{ f_n \right\}$
	such that $\|f - f_n\|_{L^\infty( [a,b], X)} \to 0$. 
\end{lemma}
%
%
\begin{proof}
  Fix $n \in \mathbb{N}$. Since $f$ is continuous, for every $t \in
\left[ a,b \right]$ there is an open set $V_t \in [a,b]$ such that
$\|f(x) - f(y)) \|_X \le 1/n$ for all $x, y \in V_t$. Note that $\left\{ V_t
\right\}_{t \in \left[ a,b \right]}$ is an open cover of $[a,b]$. We assume
without loss of generality that this cover is disjoint (since for any two
intervals $A$ and $B$ which overlap, we can replace $A$ with $A \setminus
B$ and still remain with an open cover of $[a,b]$). 
Due to the compactness of $[a,b]$, we can extract
a finite subcover $\left\{ (t_j, t_{j +1}) \right\}$ of $[a,b]$. This subcover
will be disjoint, since the original covering of $[a,b]$ was assumed to be
disjoint. Furthermore,
observe that if $t \in (t_{j}, t_{j+1})$,
then $(t_{j}, t_{j+1}) \in V_{t}$. For each interval $(t_j, t_{j +1})$
choose any $t_{j}^* \in (t_{j}, t_{j +1})$, and define the step-function
%
%
\begin{equation*}
	\begin{split}
		f_n(t) =
		\begin{cases}
      f(t_{j}^{*}), \quad & t \in (t_{j},t_{j+1}) \subset V_{t}
		\\
		0 & \text{otherwise}.
	\end{cases}
	\end{split}
\end{equation*}
%
Fix $t \in [a,b]$. By construction, $t \in V_{t}$ and
$t \in (t_{j}, t_{j+1})$ for some $j$. Hence, picking $s \in (t_{j},
t_{j+1})$, we have $s \in V_{t}$ and so
%
%
\begin{equation*}
	\begin{split}
		\|f(t)-f_n(t)\|_X
    & = \| f(t) - f(t_{j}^{*}) + f(t_{j}^{*}) - f_{n}(t)  \|_{X}
    \\
    & \le \| f(t) - f(t_{j}^{*}) \|_{X} + \| f(t_{j}^{*}) - f_{n}(t) \|_{X}
    \\
    & = \| f(t) - f(t_{j}^{*}) \|_{X}
    \\
    & \le \frac{1}{n}.
	\end{split}
\end{equation*}
%
%
Since $t$ was chosen arbitrarily, the proof is complete. 
\end{proof}
%
\begin{framed}
\begin{remark}
  \label{rem:unif}
If $f_{n}: [a,b] \to X$ is any sequence of step functions converging pointwise
in $t$ to $f$ in $X$, it converges \emph{uniformly} in $t$, due to the
compactness of $[a,b]$. 
\end{remark}
\end{framed}
%
\begin{definition}[Banach Space Integration for Continuous Functions]
  \label{def:banach}
  Let $X$ be a Banach space, $f: [a,b] \to X$ continuous, and $f_{n} \to f$ in
  $L^{\infty}([a,b], X)$. Then 
  %
  %
  \begin{equation*}
  \begin{split}
    \int_{a}^{b} f(t) dt \doteq \lim_{n \to \infty} \int_{a}^{b} f_{n}(t) dt
  \end{split}
  \end{equation*}
  %
  %
\end{definition}
%
where the convergence is in the topology of $X$. We now show that this
definition for Banach space integration is
well-defined. More precisely, we will first show that $\int_{a}^{b}
f_{n}(t) dt$ is Cauchy in $X$. Then, we will show the convergence is independent
of the step functions chosen. Proceeding, we first prove the following lemma.
%
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%                tri inequality
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\begin{lemma}
  For a step function $f: [a,b] \to X$, we have
  %
  %
  \begin{equation*}
  \begin{split}
    \| \int_{a}^{b} f(t) dt \|_{X} \le \int_{a}^{b} \| f(t) \|_{X} dt.
  \end{split}
  \end{equation*}
  %
  %
\label{lem:tri-ineq-int}
\end{lemma}
%
%
%
%
\begin{proof}
%
%
\begin{equation*}
\begin{split}
  \| \int_{a}^{b} f(t) dt \|_{X} &
  = \| \sum_{j=1}^{m}\alpha_{j} (t_{j+1} - t_{j})
  \|_{X}
  \\
  & \le  \sum_{j=1}^{m} \| \alpha_{j} \|_{X} (t_{j+1} - t_{j})
  \\
  & = \int_{a}^{b} \| f(t) \|_{X} dt
\end{split}
\end{equation*}
%
which completes the proof.
%
\end{proof}
%
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%                uniqueness
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
Definition \ref{def:banach} is then well-defined due to the following two
lemmas.
%
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%                conv
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\begin{lemma}[Convergence] Let $f_{n}: [a,b] \to X$ be a sequence of simple
  functions converging to $f$ in $L^{\infty}([a,b], X)$. Then
  %
  %
  \begin{equation*}
  \begin{split}
    \int_{a}^{b}f_{n}(t) dt
  \end{split}
  \end{equation*}
  %
  %
  is Cauchy in $X$. 
\label{lem:conv}
\end{lemma}
%
%
%
%
\begin{proof}
  \begin{equation}
    \begin{split}
  \| \int_{a}^{b} f_{n}(t) dt - \int_{a}^{b} f_{m}(t) dt \|_{X}
  & = \| \int_{a}^{b}\left[ f_{n}(t) - f_{m}(t) \right]dt \|_{X}, \quad \text{Lemma
  \ref{lem:indep-part}}
  \\
  & \le \int_{a}^{b} \| f_{n}(t) - f_{m}(t) \|_{X} dt,
  \quad \phantom{m} \text{Lemma \ref{lem:tri-ineq-int}}
  \\
  & \le \int_{a}^{b} (\| f(t) - f_{n}(t) \|_{X} + \| f(t) - f_{m}(t) \|_{X})dt.
\end{split}
\end{equation}
%
Fix $\ee$. By Remark \ref{rem:unif}, we see that there exists $N$ such
that for $m, n > N$
%
%
\begin{equation*}
\begin{split}
& \| f(t) - f_{n}(t) \|_{X} \le \ee, \quad \forall t \in [a, b].
\\
& \| f(t) - f_{m}(t) \|_{X} \le \ee, \quad \forall t \in [a, b].
\end{split}
\end{equation*}
Hence,
%
%
\begin{equation*}
\begin{split}
\| \int_{a}^{b} f_{n}(t) dt - \int_{a}^{b} f_{m}(t) dt \|_{X} \le 2(b-a) \ee,
\quad m,n > N.
\end{split}
\end{equation*}
%
Since $\ee$ can be chosen arbitrarily small, the proof is complete.
\end{proof}
%
%
\begin{lemma}[Independence]
  Let $f_{n}(t)$, $g_{n}(t) : [a,b] \to X$
  be two step functions converging to $f$ in $L^{\infty}([a,b], X)$.
  If
  %
  %
  \begin{equation*}
  \begin{split}
    & \int_{a}^{b} f_{n}(t) dt \xrightarrow{X} F
    \\
    & \int_{a}^{b} g_{n}(t) dt \xrightarrow{X} G
  \end{split}
  \end{equation*}
  %
  %
  then
  %
  %
  \begin{equation*}
  \begin{split}
    F =G.
  \end{split}
  \end{equation*}
  %
  %
\label{lem:well-def}
\end{lemma}
%
%
%
%
%
%
\begin{proof}
%
%
\begin{equation*}
\begin{split}
  \| F - G \|_{X} & = \| \int_{a}^{b} f(t) dt - \int_{a}^{b} g(t) dt \|_{X}
  \\
  & = \| \int_{a}^{b}\left[ f(t) - g(t) \right]dt \|_{X}, \quad \text{Lemma
  \ref{lem:indep-part}}
  \\
  & \le \int_{a}^{b} \| f(t) - g(t) \|_{X} dt,
  \quad \phantom{m} \text{Lemma \ref{lem:tri-ineq-int}}
  \\
  & \le \int_{a}^{b} (\| f(t) - f_{n}(t) \|_{X} + \| f(t) - g_{n}(t) \|_{X})dt.
\end{split}
\end{equation*}
%
%
Fix $\ee$. By Remark \ref{rem:unif}, we see that there exists $N$ such
that for $n > N$
%
%
\begin{equation*}
\begin{split}
& \| f(t) - f_{n}(t) \|_{X} \le \ee, \quad \forall t \in [a, b]
\\
& \| f(t) - g_{n}(t) \|_{X} \le \ee, \quad \forall t \in [a, b].
\end{split}
\end{equation*}
%
%
Hence
%
%
\begin{equation*}
\begin{split}
\| F - G \|_{X} \le 2(b-a) \ee.
\end{split}
\end{equation*}
%
%
Since $\ee$ can be chosen arbitrarily small, we see that we must have $F = G$.
\end{proof}
%
%
We conclude the section by proving the fundamental theorem of calculus, 
thereby establishing that Banach space integration and
differentiation are inverse operations. We shall need the following lemma.
%
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%                int prop
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\begin{lemma}
  Let $X$ be a Banach space, and suppose $f: [a,b] \to X$ is continuous. Then for
  $a \le b \le c$ 
%
%
\begin{equation*}
\begin{split}
  \int_{a}^{c} f(t) dt = \int_{a}^{b} f(t) dt + \int_{b}^{c} f(t) dt.
\end{split}
\end{equation*}
%
%
\label{lem:int-splitting}
\end{lemma}
%
%
%
%
\begin{proof}
  %
  Since $\| f - f_{n} \|_{L^{\infty}\left( [a,b], X \right)} \to 0$ for some sequence
  $f_{n}$ of simple functions, we have
  %
  \begin{equation*}
  \begin{split}
    \int_{a}^{c} f(t) dt = \lim_{n \to \infty} \int_{a}^{c} f_{n}(t) dt.
  \end{split}
  \end{equation*}
  %
  %
  Recall that the value of $\int_{a}^{c}f_{n}(t) dt$ does not depend upon the
  partioning we use for $f_{n}(t)$. Partition $f_{n}$ such that
  \begin{equation}
    \begin{split}
  & f_{n}(t) = f_{n, [a,b]} + f_{n, (b, c]},  
    \\
    & f_{n, [a,b]}(t) =0, \quad b< t \le c, \quad f_{n, (b, c]}(t) = 0, \quad
    a \le t \le b.
\end{split}
\end{equation}
Then
  %
  %
  \begin{equation*}
  \begin{split}
    \int_{a}^{c} f_{n}(t) dt & = \int_{a}^{c} f_{n, [a,b]}(t)dt  +
    \int_{a}^{c} f_{n, (b,c]}(t)dt 
    \\
    & = \int_{a}^{b} f_{n}(t)dt  +
    \int_{b}^{c} f_{n}(t)dt.
  \end{split}
  \end{equation*}
  %
  %
Hence 
 %
 %
 \begin{equation*}
 \begin{split}
   \int_{a}^{c} f(t) dt 
   & = \lim_{n \to \infty} \int_{a}^{c} f_{n}(t) dt
   \\
   &= \lim_{n \to \infty} \left ( \int_{a}^{b} f_{n}(t)dt  +
    \int_{b}^{c} f_{n}(t)dt \right )
    \\
    & =\int_{a}^{b} f(t) dt + \int_{b}^{c} f(t) dt
 \end{split}
 \end{equation*}
 %
 %
which concludes the proof.
\end{proof}
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%                FTC
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\begin{lemma}[Fundamental Theorem of Calculus]
Let $f \in C\left( [a,b], X \right)$, where $X$ is a Banach space. For $a \le x
\le b$, let
%
%
\begin{equation*}
\begin{split}
  F(t) = \int_{a}^{t}f(s)ds.
\end{split}
\end{equation*}
%
%
Then the map $t \mapsto F(t)$ is Lipschitz continuous from $[a,b]$ to $X$.
Furthermore, $F$ is differentiable at all $t_{0} \in [a,b]$, and
%
%
\begin{equation}
  \label{fund-thm-calc-diff}
\begin{split}
  F'(t_{0})= f(t_{0}).
\end{split}
\end{equation}
\label{lem:fund-thm-calc}
\end{lemma}
%
%
%
%
\begin{proof}
We first establish the Lipschitz continuity of the map $t \mapsto F(t)$. Assume without
loss of generality that $t_{1} \le t_{2}$. We have
%
%
\begin{equation*}
\begin{split}
  \| F(t_{1}) - F(t_{2}) \|_{X}
  & = \| \int_{a}^{t_{1}}f(s)ds -
  \int_{a}^{t_{2}} f(s)ds \|_{X}
  \\
  & = \| \int_{t_{1}}^{t_{2}} f(s) ds \|_{X}, \quad \text{Lemma
  \ref{lem:int-splitting}}
  \\
  & \le \int_{t_{1}}^{t_{2}}\| f(s) \|_{X} ds.
\end{split}
\end{equation*}
%
%
Since $[a,b]$ is compact and $f$ is continuous, we have $\| f(s) \|_{X} \le M$
for all $s \in [a,b]$. Hence
%
%
\begin{equation*}
\begin{split}
  \| F(t_{1}) - F(t_{2}) \| \le M(t_{2} - t_{1})
\end{split}
\end{equation*}
%
%
which establishes the Lipschitz continuity of the map $t \mapsto F(t)$. To
establish \eqref{fund-thm-calc-diff}, we apply the definition of Banach space
differentiation given in \eqref{diff-limit-simp} and see that
%
%
\begin{equation*}
\begin{split}
   \| \frac{F(t_{0} + h) - F(t_{0})}{h}  - f(t_{0}) \|_{X}
  & = \| \frac{\int_{a}^{t_{0}+h}f(s)ds - \int_{a}^{t_{0}}f(s)ds}{h} -
  f(t_{0}) \|_{X}
  \\
  & = \| \int_{a}^{t_{0}+h}\frac{f(s)}{h}ds  -
  \int_{t_{0}}^{t_{0} + h} \frac{f(t_{0})}{h} ds \|_{X}
  \\
  & = \frac{1}{h} \| \int_{t_{0}}^{t_{0} + h}[f(s) - f(t_{0})]ds \|_{X}, \qquad
  \text{Lemma \ref{lem:int-splitting}}
  \\
  & \le \frac{1}{h} \int_{t_{0}}^{t_{0} + h} \| f(s) - f(t_{0})
  \|_{L^{\infty}\left( [t_{0}, t_{0} + h], X \right)}
  \\
  & = \| f(s) - f(t_{0})
  \|_{L^{\infty}\left( [t_{0}, t_{0} + h], X \right)}
  \\
  & = \lim_{h \to 0} \sup_{0 \le k \le 1} \| f(t_{0} + kh) - f(t_{0})
  \|_{X}.
\end{split}
\end{equation*}
%
%
Note that since $f$ is continuous on $[a,b]$, and $[a,b]$ is compact, it follows
that $f$ is uniformly continuous on $[a,b]$. Hence, for fixed $\delta > 0$,
there exists $\ee_{\delta} > 0$ such that for $h < \ee_{\delta}$, we have
%
%
\begin{equation*}
\begin{split}
  \| f(t_{0} + kh) - f(t_{0}) \|_{X} < \delta, \ \text{for all } \  0 \le k \le 1.
\end{split}
\end{equation*}
%
%
Hence
%
%
%
\begin{equation*}
\begin{split}
  \sup_{0 \le k \le 1} \| f(t_{0} + kh) - f(t_{0}) \|_{X} < \delta, \quad h <
  \ee_{\delta}.
\end{split}
\end{equation*}
%
%
Since $\delta$ can be chosen arbitrarily small, we conclude that
%
\begin{equation*}
\begin{split}
  \lim_{h \to 0} \sup_{0 \le k \le 1} \| f(t_{0} + kh) - f(t_{0})
  \|_{X} = 0,
\end{split}
\end{equation*}
%
%
concluding the proof.
\end{proof}
%
%
%
%
%
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%				 Contraction Mapping Theorem
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\section{Contraction Mapping Lemma}
\begin{definition}
  Let $\left( X, d \right)$ be a metric space. A mapping $T: X \to X$ is called a
\emph{contraction} if there exists an $\alpha$, $0 < \alpha <1$ such that
%
%
\begin{equation*}
	\begin{split}
		d(Tx, Ty) \le \alpha d(x,y), \qquad \forall x, y \in X.
	\end{split}
\end{equation*}
%
\end{definition}
%
\begin{framed}
\begin{remark}
	Observe that a contraction mapping is always continuous.
\end{remark}
\end{framed}
%
%
\begin{framed}
\begin{example}
	The function $T(x) = 0.1x^2$ defines a contraction mapping in the set 
	$X = [-4, 4]$ equipped with the metric $d(x,y) = |x-y|$. 
\end{example}
\end{framed}
	%
	%
	%
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%
	%				Banach Space Fixed Point Theorem 
	%
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	%
	\begin{lemma}[Contraction Mapping Lemma]
		\label{lem:fixed-point}
	Let $(X,d)$ be a complete metric space, and $T: X \to X$ a contraction
	mapping. Then $T$ has a unique fixed point in $X$. That is, there is a unique
	point $x^* \in X$ such that $Tx^* = x^*$. Furthermore, if $x_0$ is any point
  in $X$, and we define the sequence $x_{n+1} = Tx_n$, then $x_n \xrightarrow{X} x^*$ as $n
	\to \infty$.
	\end{lemma}
	%
	%
  \begin{proof} First we show uniqueness. If $x^*$ and $x^{**}$ are two fixed
	points, then
	%
	%
	\begin{equation*}
		\begin{split}
			d(x^*, x^{**}) = d(Tx^*, Tx^{**}) \le \alpha d(x^*, x^{**}) \implies d(x^*,
			x^{**}) = 0 \implies x^* = x^{**}.
		\end{split}
	\end{equation*}
	%
	%
To prove existence, we observe that since $X$ is complete it suffices to show
that $x_n$ is Cauchy. A repeated application of the
contraction inequality gives
%
%
\begin{equation*}
	\begin{split}
		d\left( x_{n+1},x_n \right)
		& = d\left( Tx_n, Tx_{n-1} \right)
		\\
		& \le \alpha d\left( x_n, x_{n-1} \right)
		\\
		& \le \alpha^2 d\left( x_{n-1}, x_{n-2} \right)
		\\
		& \cdots
		\\
		& \le \alpha^n d\left( x_1, x_0 \right).
	\end{split}
\end{equation*}
%
%
Hence
%
%
\begin{equation*}
\begin{split}
  d\left( x_{n+k},x_n \right)
  & \le (\alpha^{n } +\alpha^{n+1} + \cdots +
  \alpha^{n+k-2} + \alpha^{n+k-1})d(x_{1}, x_{0}) 
  \\
  & = \alpha^{n}(1 + \alpha + \cdots + \alpha^{k-2} + \alpha^{k-1})
  \\
  & \le \alpha^{n}\left( \frac{1}{1 - \alpha} \right)
  \\
  & \to 0 \ \text{as} \ n \to \infty
\end{split}
\end{equation*}
%
%
since $0 < \alpha < 1$. 
\end{proof}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%				 Proof of ODE Theorem
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\section{Proof of \hyperref[ode-thm]{Metric Space ODE Theorem}}
	%
	%
	Since $f(t)$ is Lipschitz continuous on $E$ for $t \in (-a, a)$, it is
	continuous on $E$. Hence, using the theory of Banach space integration
  developed earlier and the fundamental theorem of calculus,
  one can check that for $t \in (-a, a)$, the initial value problem
  \eqref{ode-thm-eq}-\eqref{ode-thm-init-data} is equivalent to the
	integral equation
	%
	%
	\begin{equation*}
		\begin{split}
			u(t) = u_0 + \int_0^t f(s, u(s) ) \ ds.
		\end{split}
	\end{equation*}
	%
	%
	%
	%
	Let $[-h, h] \subset (-a, a)$ be a closed interval,
	and choose $r$ such that
	$$B_r(u_0) \doteq \left\{ u \in X: d(u_0, u) \le r \right\}$$
	is a subset of $E$. Define 
	$$V_h = \left\{ \text{all maps} \; \;  v: [-h, h]
		\to B_r(u_0)\right\}.$$ Then $V_h$ is a Banach
		space under the norm defined by $$| | | v_1 - v_2 | | | = \sup_{s \in [-h,
    h]} d[v_1(s),v_2(s)].$$ Let $T$ be a map
	acting on $V_h$ via the relation $$Tv(t) = u_0 + \int_0^t f(s, v(s) ) \ ds.$$
	Recalling \autoref{lem:fixed-point}, we see that to complete the proof it will be enough to show that $T$ is a contraction on
	$V_h$, for suitably small $h >0$. First, note that for $v \in V_h$, we have
	%
	%
\begin{equation}
	\label{cont-map-into}
	\begin{split}
		| | | Tv - u_0| | |
		& = | | | \int_0^t f(s, v(s) ) \ ds | | |
		\\
		& \le  \int_0^t | | | f(s, v(s) ) | | | ds
		\\
		& \le   \int_0^t M_1 ds
		\\
		& =  t M_1
		\\
		& \le  h M_1.
	\end{split}
\end{equation}
%
%
Choosing $h \le r/M_1$, it follows that $T: V_h \to V_h$. 
%Since $[-h, h] \subset (-a, a)$, we can find a compact set $C$ such that $(-h,
%h) \subset C \subset (-a, a)$. Since $f$ is a continuous function of two
%variables, $f( (C \times K) )$ is compact, and so \eqref{cont-map-into} gives
%the estimate
%%
%%
%\begin{equation*}
%	\begin{split}
%		| | | Tv | | | \le \|u_0\|_X + Mh < \infty
%	\end{split}
%\end{equation*}
%
%
Next, note that for any two points $v_1, v_2 \in
V_h$, we have
%
%
\begin{equation}
	\label{cont-part-1}
	\begin{split}
		| | | Tv_2 - Tv_1 | | | 
		& = | | | \int_0^t \left[ f(s, v_2(s) ) - f(s, v_1 (s) ) \right]ds | | |
		\\
		& \le \int_0^t | | | f(s, v_2(s) ) - f(s, v_1 (s) ) | | | ds
		\\
		& = \int_0^t \sup_{s \in [-h, h]} d[f(s, v_1(s) ), f(s, v_2 (s) )] \ ds
		\\
		& \le \int_0^t M_2 \sup_{s \in [-h, h]} d[v_1(s), v_2 (s)] \
		ds
		\end{split}
\end{equation}
%
%
where the last step follows from \eqref{stronger-ode}.
Hence
\begin{equation*}
	\begin{split}
		| | | Tv_2 - Tv_1 | | | 
		& \le M_2 h \sup_{s \in [-h, h]} d[v_1(s), v_2 (s)]
		\\
		& = M_2 h   | | | v_2 - v_1 | | |_X.  
	\end{split}
\end{equation*}
%
%
Restricting $h < 1/(M_2)$, we obtain
\begin{equation*}
	\begin{split}
		| | | Tv_2 - Tv_1 | | | & \le c | | | v_2 - v_1 | | |_X, \qquad c <1. 
	\end{split}
\end{equation*}
Hence, for $h < \min\left\{r/M_1, 1/M_2  \right\}$, $T$ is a contraction on
$V_h$.  This completes \\ the proof. \qed
%
%
\appendix
\section{Differentiation in Banach Spaces}
We remark that the theory presented below can be extended to arbitrary complete
metric spaces (and hence, Fr\'echet spaces) by replacing norms with metrics.
\begin{definition}
	\label{def:diff}
	Let $X,Y$ be Banach spaces over the real numbers, and consider the map $f: X \to Y$.
	Then $f$ is differentiable at $x_0$ if there
	is a continuous linear map $Df(x_0): X \to Y$ such that
	%
	%
	%
	%
	\begin{equation}
		\label{diff-limit}
		\begin{split}
			\lim_{h \to 0} \frac{\|f(x_0+ h) - f(x_0) -
			Df(x_0)(h) \|_Y}{\|h\|_{X}} = 0
		\end{split}
	\end{equation}
	%
	%
	This map, which we call the \emph{total derivative} of $f$ at $t_0$, is 
	unique. If $Df(x_0)$ exists for all $x_0 \in X$,
	then we say that $f$ is
	\emph{differentiable} in $X$. If $f$ is differentiable in $X$, and 
	$\|Df(x_0 + h) - Df(x_0) \|_Y \to 0$ as $\|h\|_{X} \to 0$ for all $x_0 \in X$,
	then we say that $f$ is \emph{continuously differentiable in $X$}. If $X, Y$
  are Banach spaces over the complex numbers, we say that $f$ is
  \emph{holomorphic} (or \emph{continuously holomorphic}) in $X$.
\end{definition}
	%
  %
  %
  \begin{framed}
  %
  %
  \begin{remark}
    Equivalently, $f$ is differentiable at $x_{0}$ is there exists a continuous
    linear map $Df(x_{0}): X \to Y$ such that
    %
    %
    \begin{equation*}
    \begin{split}
      f(x_{0} + h) = f(x_{0}) + Df(x_{0}) \circ h + o(\| h \|_{X}).
    \end{split}
    \end{equation*}
    %
    To see this, suppose
    %
    %
    \begin{equation*}
    \begin{split}
      \lim_{h \to \infty} \frac{\| f(x_{0} + h) - f(x_{0}) - Df(x_{0}) \circ h
      \|_{Y}}{\| h \|_{X}} = 0.
    \end{split}
    \end{equation*}
    %
    %
    Then we can find $\delta > 0$ such that
    %
    %
    \begin{equation*}
    \begin{split}
    \frac{\| f(x_{0} + h) - f(x_{0}) - Df(x_{0}) \circ h
      \|_{Y}}{\| h \|_{X}}  < \ee
    \end{split}
    \end{equation*}
    %
    %
    for all $h \in X$ with $\| h \|_{X} < \delta$. Hence
    %
    %
    \begin{equation*}
    \begin{split}
      \| f(x_{0} + h) - f(x_{0}) - Df(x_{0}) \circ h \|_{Y} < \ee \| h
      \|_{X}.
    \end{split}
    \end{equation*}
    %
    %
    This implies
    %
    %
    \begin{equation*}
    \begin{split}
      f(x_{0} + h) - f(x_{0}) - Df(x_{0}) \circ h = g, \quad g \in Y, \ \| g
      \|_{Y} < \ee \| h \|_{X}.
    \end{split}
    \end{equation*}
    %
    %
    Hence, 
    %
    %
    \begin{equation*}
    \begin{split}
      f(x_{0} + h) 
      & = f(x_{0}) + Df(x_{0}) \circ h + g
      \\
      & =  f(x_{0}) + Df(x_{0})\circ h + o(\| h \|_{X}).
    \end{split}
    \end{equation*}
    %
    %
    For the reverse direction, if
    %
    %
    \begin{equation*}
    \begin{split}
      f(x_{0} + h) = f(x) + Df(x_{0}) \circ h + o(\| h \|_{X})
    \end{split}
    \end{equation*}
    %
    %
    then
    %
    %
    \begin{equation*}
    \begin{split}
      \| f(x_{0} + h) - f(x_{0}) - Df(x_{0}) \circ h \|_{Y} = o(\| h
      \|_{X})
    \end{split}
    \end{equation*}
    %
    %
    which implies
    %
    %
    \begin{equation*}
    \begin{split}
      \lim_{h \to \infty} \frac{\| f(x_{0} + h) - f(x_{0}) - Df(x_{0}) \circ h
      \|_{Y}}{\| h \|_{X}}  = \lim_{h \to \infty} \frac{o(\| h \|_{X})}{\| h
      \|_{X}} = 0.
    \end{split}
    \end{equation*}
    %
    %
    %
  \label{rem:equiv-def}
  \end{remark}
  %
  %
  \end{framed}
  %
  %
  \begin{framed}
	\begin{remark}
		\label{rem:usual-diff}
		Consider the map $f: \rr \to \rr$. Then \autoref{def:diff} 
		coincides with the usual definitions of
		differentiability and continuous differentiability for maps
		from $\rr $ to $\rr$.
		To see this, assume $f$ is differentiable at $x_0$.
		Let us first verify that the map  $D(x_0): \rr ~\to~\rr$
		defined by $Df(x_0)(x) =
		xf'(x_0)$ is the total derivative of $f$. Assume without loss of generality
		that $h \to 0^+$. Then
		%
		%
		\begin{equation}
			\label{2}
			\begin{split}
				 \lim_{h \to 0^+} \frac{| f( x_0 + h) - f(x_0) -
				Df(x_0)(h) |}{|h|}
				 & = \lim_{h\to 0^+} \left |\frac{f(x_0+h) -
				f(x_0)}{h} - \frac{Df(x_0)(h)}{h}  \right |
				\\
				 & =\lim_{h \to 0^+} \left |\frac{f(x_0+h) - f(x_0)}{h} -
				f'(x_0) \right | = 0.
			\end{split}
		\end{equation}
		%
		%
%
%
For any $a \in \rr$, define the map $T_{a} \in L(\rr , \rr)$ by
$T_{a}(x) = ax$. Then the map $a \mapsto T_a$ is an isometric
isomorphism from $\rr$ to $L( \rr, \rr)$. Hence, 
we may identify $f'(x_0)$ with $T_{f'(x_0)} = Df(x_0)$,
which by \eqref{2} is the total derivative of $f$.  Using this identification,
it follows that $f$ is continuously
differentiable in $\rr$ if and only if $f'$ is a continuous function of
$x_0$, for all $x_0 \in \rr$. \qed
%
\end{remark}
\end{framed}
%
%
In general, for an arbitrary Banach space $X$, open interval $(a,b) \subset
\rr$, and map $f:(a,b) \to X$, we can identify $Df(x_0)$ with an
element of $X$ via the following.
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%			Lemma Isometry	
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\begin{lemma}
	\label{lem:isometry} Let $(a,b) \subset \rr$ be an open interval, $X$ a Banach
	space, with $x \in X$. Define the map $T_x \in L\left ( (a,b) , X \right )$ by
	$T_x(t_0) = x t_0$. Then the map $x \mapsto T_x$ is an
	isometric isomorphism from
	$X$ to $L((a,b) , X)$. 
\end{lemma}
%
%
\begin{proof} Note that 
%
%
\begin{equation*}
	\begin{split}
		| | | T_x | | |
		& = \sup_{|t_0| = 1} \| T_x (t_0) \|_X
		= \| x t_0\|_X
		= \|x\|_X.
	\end{split}
\end{equation*}
%
%
Hence, the map $x \mapsto T_x$ is an isometry from $X$ into $L((a,b),
X)$. It remains to show that it is onto. Let $U \in L( (a,b), X)$. Then
by linearity
%
%
\begin{equation*}
	\begin{split}
		U(t_0) = U(1)t_0. 
	\end{split}
\end{equation*}
%
%
Hence, $U = T_{U(1)}$, completing the proof. 
\end{proof}
%
%
Applying the lemma, we see that if $Df(t_0)$ exists for a map $f: (a,b) \to X$,
then it can be viewed as an
element of $X$. Similarly, if $Df(t_0)$ exists for all $t_0 \in (a,b)$, then
we may view the map $t_0 \to Df(t_0)$ as an
element of $L( (a,b), X)$. Hence, for a
map $f:(a,b) \to X$, we see that the following is an equivalent
reformulation of \autoref{def:diff}. 
\begin{definition}
	\label{def:diff-simp}
	Let $X$ be Banach space, $(a,b) \subset \rr$ an open interval, and
	consider the map $f: (a,b) \to X$.
	Then $f$ is \emph{differentiable at $t_0$} if there exists a map
	$f': (a,b) \to X$ such that 
	%
	%
	%
	%
	\begin{equation}
		\label{diff-limit-simp}
		\begin{split}
			\lim_{h \to 0} \| \frac{f(t_0+ h) - f(t_0) 
			 }{h} - f'(t_0) \|_X = 0.
		\end{split}
	\end{equation}
	%
	%
	We call $f'(t_0)$ the \emph{derivative of $f$ at $t_0$}.
	If \eqref{diff-limit-simp}
	holds for all $t_0 \in (a,b)$, then we say $f$ is \emph{differentiable in
	$(a,b)$}, and call $f'$ the
	\emph{derivative of $f$ in $(a,b)$}.  
\end{definition}
\begin{framed}
\begin{example}
Let $f: (a,b) \to \rr^2$ be defined by $f(t) = (1, t^2)$. Then $Df(1)$ maps
$(a,b)$ to $\rr$ by the relation $Df(1)(t) = (0, 2t) = t[0, 2]$. Hence, $Df(1)$ is the $1
\times 2$ matrix $[0,2]$, which we may also view as the point $(0,2) \in \rr^2$.
That is, $f'(1) = (0,2)$. Similarly, $f'(t) = (0,2t)$.
\end{example}
\end{framed}

Lastly, we include the following.
%
%
\begin{proposition}
		(Chain Rule) Let $X,Y,Z$ be Banach spaces, $g: Y \to Z$ and $f:
		X \to Y$ continuously differentiable maps. Then for all $x_0
		\in X$ we have \begin{equation*} (g \circ f)' (x_0) =
			g'(f(x_0)) \circ (f'(x_0)).
		\end{equation*} 
	\end{proposition}
  \begin{proof} Choose $0<\ee<1$. Since 
			\begin{equation*}
				\lim_{s \to 0} \frac{\|f (x_0 + s) - f(x_0) -
				f'(x_0)(s)\|}{\|s\|} = 0
			\end{equation*}
			we can find $\delta > 0$ such that 
			\begin{equation*}
				\frac{\|f (x_0 + s) - f(x_0) -
				f'(x_0)(s)\|}{\|s\|} < \ee
			\end{equation*}
			for $\|s\| < \delta$. This implies
			\begin{equation*}
				\|f(x_0 + s) - f(x_0) - f'(x_0)(s) \| < \ee \|s\|.
			\end{equation*}
			Hence, we can write
			\begin{equation*}
				f(x_0 + s) = f(x_0) + f'(x_0)(s) + o_{1}(s)
			\end{equation*}
			with $\|o_{1}(s)\| < \ee \|s\|$. Similarly, for $\|t\| <
			\delta$ we have 
			\begin{equation*}
				g(x_0 + t) = g(x_0) + g'(x_0)(t)+ o_{2}(t)
			\end{equation*}
			with $\|o_{2}(t)\| < \ee \|t\|$. In addition, since $f'(x_0)$
			and $g'(f(x_0))$ are continous linear operators, we have
			\begin{equation*}
				\begin{split}
					&\|f'(x_0)(s) \| < a \|s \|,
					\\
					&\|g'(x_0)(t) \| < b \|t \|
				\end{split}
			\end{equation*}
			for some constants $a , b$. Hence
			\begin{equation*}
				\|f'(x_0)(s) + o_{1}(s) \| < (a + 1) \|s\|
			\end{equation*}
			for $\|s\| < \delta$. Then for $\|s \| <
			\delta/(a+1)$ we have
			\begin{equation}
				\label{key_estimate}
				\begin{split}
					&\| o_{2} [f'(x_0)(h) + o_{1}(s)] \| < \ee(a+1)\|s \|,
					\\
					& \|g'(f(x_0))(o_{1}(s))\| < b \ee \|s\|.
				\end{split}
			\end{equation}
			Hence
			\begin{equation*}
				\begin{split}
					h(x_0 + s) &= g(f(x_0 +s)
					\\
					&= g(f(x_0) + f'(x_0)(s) + o_{1}(s))
					\\
					&= g(f(x_0)) + g'(f(x_0))(f'(x_0)(s) + o_{1}(s)) 
					+ o_{2}(f'(x_0)(s) + o_{1}(s))
					\\
					&= g(f(x_0)) + g'(f(x_0))f'(x_0)(s) +
					g'(f(x_0))(o_{1}(s)) + o_{2}(f'(x_0)(s) + o_{1}(s))
				\end{split}
			\end{equation*}
			Applying \eqref{key_estimate}, we conclude that
			\begin{equation*}
				\begin{split}
				&h(x_0 + s) = g(f(x_0)) + g'(f(x_0))(f'(x_0)(s)) +
				O_3(s), \; 
			\text{where}
				\\
				&\|O_3(s)\| < (a + b + 1) \ee \|s\|
			\end{split}
			\end{equation*}
     completing the proof. 
   \end{proof}
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%                Dependnece on Params
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\section{Persistence of Regularity for ODEs} 
\label{sec:dep-param}
%
%
Following Taylor \cite{Taylor:1995kx}, let $X$ be a Banach space, $U \subset X$ an open subset, and $F: U \to X$. Consider the non-autonomous system
%
%
\begin{gather}
  \label{aa}
\frac{dy}{dt} = F(y(x,t), t),
\\
y(0)= y_{0}(x) \in X, \quad x \in \ci^{n} \ \text{or} \ \rr^{n},t \in \rr.
\label{bb}
\end{gather}
%
Letting $z = (y(x,t), t)$, we get
%
%
\begin{equation*}
\begin{split}
\frac{dz}{dt}  
& = \left (\frac{dy}{dt}, 1 \right )
\\
& = \left( F(y(t), t), 1 \right)
\\
& = \left( F(z), 1 \right)
\\
& \doteq G(z).
\end{split}
\end{equation*}
%
%
Hence, without loss of generality, we may restrict our attention to the
autonomous system
%
%
\begin{gather}
\frac{dy}{dt} = F\left( y(x,t) \right)
\label{ode-eq}
\\
y(0) = y_{0}(x), \quad x \in \ci^{n} \ \text{or} \ \rr^{n},t \in \rr
\label{ode-init-data}
\end{gather}
%
%
%
for which we shall prove the following.
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%                dep on init cond
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
\begin{proposition}
  Let $U \subset C^{k}$ be an open subset, $k \ge 0$. Suppose
  $F: U \to C^{k}$ is Lipschitz and $k$ times differentiable. 
  Then if $y_{0} \in C^{k}$, there exists an open set $I \subset \rr$
such that the ivp \eqref{ode-eq}-\eqref{ode-init-data}
admits a unique solution $y(x,t) \in C^{k}_{x}$ for $t \in I$. 
\label{prop:reg-result}
\end{proposition}
%
%
%
%
\begin{proof}
  We divide our work into cases.
  \subsection{Case $k = 0$.} 
  \label{ssec:case-0}
  This is just a special case of Theorem \ref{ode-thm}.
    \subsection{Case $k=1$} 
  \label{ssec:case-k}
 % 
 %
Formally differentiate
\eqref{ode-eq}-\eqref{ode-init-data} with respect to $x$ and obtain
%
%
%
\begin{gather}
  W' = DF(y) \circ W
  \label{ode-lin}
  \\
  W(0) = W_{0} 
  \label{ode-lin-init-data}
\end{gather}
%
%
where $W \doteq D_{x} y(x,t)$ and $y$ is the unique solution to
\eqref{ode-eq}-\eqref{ode-init-data}. Let $w(x,t) = D_{x}y(x,t) \circ h$, where $h \in U$ is
arbitrary. Then
from \eqref{ode-lin}-\eqref{ode-lin-init-data} we
obtain
%
%
\begin{gather}
  w' = DF(y) \circ w 
  \label{ode-lin-h}
  \\
  w(0) = DY_{0}(x) \circ h
  \label{ode-lin-init-data-h}
\end{gather}
%
%
Since $F$ is $C^{1}(U)$, $Df(y): U \to C^{1}$ continuously. Therefore, by the Banach Peano
existence theorem, there exists a solution $w = w(x,t)$ (not necessarily unique) to
\eqref{ode-lin-h}-\eqref{ode-lin-init-data-h} for $t$ in some open subset of
$\rr$. We now show that this solution is in fact $D_{x} y(x,t)$ as follows. Let
$z(x,t) = y(x + h, t) - y(x,t)$. Note that
%
%
\begin{equation}
  \label{uhh}
\begin{split}
\frac{dz}{dt} 
& = F\left[ y(x + h, t) \right] - F\left[ y(x,t) \right]
\\
& = \int_{0}^{1} \frac{d}{ds} F\left[ sy(x+h, t) + (1-s)y(x,t) \right]ds
\\
& = \int_{0}^{1} \frac{d}{ds} F\left[ sz(x,t) + y(x,t) \right] ds
\\
& = F(y+z) - F(y)
\end{split}
\end{equation}
%
%
which by the definintion of the Banach space derivative implies
%
%
\begin{equation*}
\begin{split}
  \frac{dz}{dt} = Df(y) \circ z + R_{1}(y,z), \quad R_{1}(y,z) = R_{1}[z(t)] = o(\|
  z(t) \|_{C^{1}})
\end{split}
\end{equation*}
%
%
and so
%
%
\begin{equation*}
\begin{split}
  \frac{d}{dt}(z-w) = DF(y) \circ (z-w) + R_{1}(y,z).
\end{split}
\end{equation*}
%
%
Noting that %
%
\begin{equation*}
\begin{split}
  (z-w)(0) & = y_{0}(x+h) - y_{0}(x) - Dy_{0}(x) \circ h
  \\
  & = R_{2}(x,h), \quad R_{2}(x,h) = o(| h |)
\end{split}
\end{equation*}
%
%
we seek to solve the inhomogeneous ode
%
%
\begin{gather}
  \frac{d}{dt}(z-w)  = Df(y) \circ (z-w) + R_{1}(y,z)
\label{inhom-ode}
  \\
  (z-w)(0) = R_{2}(x,h), \quad R_{2}(x,h) = o(| h |).
  \label{inhom-ode-init}
\end{gather}
%
%
To do so, we first solve the homogenous ode
\begin{gather}
  \frac{d}{dt}(z-w)  = Df(y) \circ (z-w) + R_{1}(y,z)
\label{hom-ode}
  \\
  (z-w)(0) = R_{2}(x,h), \quad R_{2}(x,h) = o(| h |).
  \label{hom-ode-init}
\end{gather}
Letting $\psi(x,t) = z(x,t) - w(x,t)$, this is equivalent to
%
%
%
\begin{gather*}
  \frac{d\psi}{dt}  = Df(y) \circ \psi + R_{1}(y,z)
  \\
  \psi(0) = R_{2}(x,h), \quad R_{2}(x,h) = o(| h |).
\end{gather*}
which admits the unique solution
%
%
\begin{equation*}
\begin{split}
  \psi(x,t) 
  & = e^{\int_{0}^{t} DF\left[ y(x,s) \right]ds} \circ R_{2}(x,h) 
  \\
  & \doteq S(t)R_{2}(x,h).
\end{split}
\end{equation*}
%
%
By Duhamel's principle, the solution to \eqref{inhom-ode}-\eqref{inhom-ode-init}
is then given by
%
%
\begin{equation*}
\begin{split}
  z(t) - w(t) = \int_{0}^{t} S(t-t') R_{1}\left[ y(x,t'), z(x,t') \right]dt'.
\end{split}
\end{equation*}
%
%
But
%
%
\begin{equation}
  \label{yui}
\begin{split}
  \|z(t) - w(t) \|_{C^{1}}
  & = \| \int_{0}^{t} S(t-t') R_{1}\left[ y(x,t'), z(x,t')
  \right]dt' \|_{C^{1}}
  \\
  & \le \int_{0}^{t} \| S(t-t') R_{1}\left[ y(x,t'), z(x,t') \right]
  \|_{C^{1}} dt'
  \\
  & \le \int_{0}^{t}  | | | S(t-t')  | | |_{L(U, C^{1})} \| R_{1}\left[ y(x,t'),
  z(x,t')
  \right] \|_{L^{\infty}\left( [0,t], C^{1} \right)} dt'
\end{split}
\end{equation}
%
%
where $\| \cdot \|_{L(U, C^{1})}$ denotes the operator norm on the space
$L(U,C^{1})$ of linear continuous functions from $U$ to $C^{1}$. We have the bound
%
%
\begin{equation}
  \label{op-norm}
\begin{split}
  | | | S(t-t') | | |_{L(U, C^{1})} 
  & = | | | e^{\int_{0}^{t-t'} DF \left[ y(x,s)
  \right] ds} | | |_{L(U, C^{1})}
  \\\
  & \le e^{\int_{0}^{t-t'} | | | DF\left[ y(x,s) \right]| | |_{L(U, C^{1})}ds} 
  \\
  & \le e^{M(t-t')}.
\end{split}
\end{equation}
%
%
We now need an estimate global in $[0,t]$ for
$$ \| R_{1}\left[ y(x,t'), z(x,t')
\right] \|_{L^{\infty}\left( [0,t], C^{1} \right)} dt'.$$ Since 
$$ \| R_{1}\left[ y(x,t'), z(x,t')
\right] \|_{L^{\infty}\left( [0,t], C^{1} \right)} dt' = o\| z(t)
\|_{C^{1}}$$ for fixed
$y$, it will be enough to bound $\| z(t') \|_{C^{1}}$ for $0 \le t' \le t$. From the
second line of \eqref{uhh}, we get
%
%
\begin{equation*}
\begin{split}
\frac{d}{dt} \| z(t) \|
& \le \| \int_{0}^{1} \frac{d}{ds} F\left[ sy(x+h, t) + (1-s)y(x,t) \right]ds
\|_{C^{1}}
\\
& \le \| \int_{0}^{1} DF\left[  sy(x+h, t) + (1-s)y(x,t) \right] \circ z ds
\|_{C^{1}}
\\
& \le \| z(t) \|_{C^{1}} | | | DF | | |_{L(U, C^{1})}
\\
& = M \| z(t) \|_{C^{1}}.
\end{split}
\end{equation*}
%
%
Hence, setting $\vp(t) =  \| z(t) \|_{C^{1}}$, we wish to solve
%
%
\begin{gather*}
\frac{d \vp}{dt} = M \vp
\\
\vp(0) = \| y_{0}(x+h) - y_{0}(x) \|_{C^{1}}
\end{gather*}
%
%
which gives
%
%
\begin{equation*}
\begin{split}
  \vp(t) & = \vp(0)e^{Mt}
  \\
  & = \| y_{0}(x+h) - y_{0}(x) \|_{C^{1}} e^{Mt}.
\end{split}
\end{equation*}
%
%
Since $y_{0}(x) \in C^{1}(U)$, $Dy_{0}(x) \in \text{C}(U)$, and so
%
%
\begin{equation*}
\begin{split}
  \vp(t) = o(|h|)
\end{split}
\end{equation*}
%
%
Hence,
%
%
\begin{equation*}
\begin{split}
  \| z(t) \|_{C^{1}}  =  o (| h | ) \ \text{for all } \ t \in I
\end{split}
\end{equation*}
%
%
and so
%
\begin{equation}
  \begin{split}
    \label{ihh}
    \| R_{1}\left[ y(x,t'), z(x,t')
    \right] \|_{L^{\infty}\left( [0,t], C^{1} \right)} dt' 
    & = o\| z(t) |_{C^{1}} 
    \\
    & = o(| h |).
  \end{split}
\end{equation}
%
%
%
Combining \eqref{yui}, \eqref{op-norm}, and \eqref{ihh}, we obtain
%
%
\begin{equation*}
\begin{split}
  \| z(t) - w(t) \|_{C^{1}} 
  & \le \int_{0}^{t} t e^{M(t - t')} o(| h
  |) dt'
  \\
  & = te^{Mt} o(| h |) \int_{0}^{t} e^{-Mt'} dt'
  \\
  & = o(| h |),
\end{split}
\end{equation*}
%
%
that is
%
%
\begin{equation*}
\begin{split}
  \| y(x + h, t) - y(x,t) - w(x,t) \|_{C^{1}} = o(| h |).
\end{split}
\end{equation*}
%
%
Hence, by the definintion of the Banach space derivative, $D_{x}y(x,t)$ exists and
is equal to $w(x,t)$. The proof for the case $k=1$ is complete.
\subsection{Case $k >1$} 
\label{ssec:case-kg1}
For finite $k$, formally differentiating \eqref{ode-eq}-\eqref{ode-init-data}
$k$ times with repsect to $x$, we obtain
\begin{gather*}
  W' = DG(y) \circ W
  \\
  W(0) = W_{0}
\end{gather*}
where $G \doteq D^{k-1}F$, $W \doteq D_{x}^{k} y(x,t)$. Hence, the proof of
$k$-\time differentiability in $x$ reduces to the proof in the case $k=1$, which
comples the proof for finite $k$. If $k = \infty$, we run an induction on $k$ to
obtain the corresponding result.
\end{proof}
%
%
We immediately obtain the following useful corollary.
%
\begin{corollary}[Regularity With Respect to Parameters]
  \label{cor:reg-param}
  Let $U \subset C^{k}$ be an open subset, $ k \ge 0$.  
Consider the ode
\begin{gather}
  \label{ode-param-naut}
\frac{dy}{dt} = F \left [ y(x, \tau, t), \tau \right]
\\
y(0) = y_{0}(x), \quad \tau, x \in \ci^{n} \ \text{or} \ \rr^{n}, t \in \rr
\label{ode-param-init-naut}
\end{gather}
%
%
where $F: U \times \rr  \to X$ is Lipschitz and $k$ times differentiable. Then
if $y_{0}(x) \in C^{k}$, there exists an 
open set $I \subset \rr$
such that the ivp \eqref{ode-param-naut}-\eqref{ode-param-init-naut}
admits a unique solution $y(x, \tau, t)$ for $t \in I$. In addition,
this solution is $C^{k}$ in $x$ and $\tau$.
%
\end{corollary}
%
\begin{proof}
  Letting $z = \left[ y(x, \tau, t), \tau \right]$, we get
  %
  %
  \begin{equation*}
  \begin{split}
  \frac{dz}{dt}
  & = \left( \frac{dy}{dt}, 0 \right)
  \\
  & = \left( F\left[ y(x,\tau, t), \tau \right], 0 \right)
  \\
  & = \left( F[y(z)], 0 \right)
  \\
  & \doteq G(z).
  \end{split}
  \end{equation*}
  %
  Hence, without loss of generality, we restrict our attention to the ivp
\begin{gather}
  \label{ode-param}
\frac{dy}{dt} = F \left [ y(x, \tau, t) \right]
\\
y(0) = y_{0}(x) \in C^{k}, \quad \tau, x \in \ci^{n} \ \text{or} \
\rr^{n}, t \in \rr.
\label{ode-param-init}
\end{gather}
  %
  The idea will be to view the couple
  $(x, \tau)$ as the spatial component of the ode
  \eqref{ode-param}-\eqref{ode-param-init}.
  To make this rigorous, let $z = (x, \tau)$. Then
  \eqref{ode-param}-\eqref{ode-param-init} is equivalent to the system
  %
  %
  \begin{gather*}
    \frac{d}{dt}(y, z) = \left( F[y(z,t)], \vec{0} \right), \quad \vec 0 =
    (0, 0)
  \\
  (y, z)(0) = \left ( y_{0}(x), \tau \right ).
  \end{gather*}
  %
  %
  Letting $Y = (y,z)$, and $G: U \times \left\{ \vec{0} \right\} 
  \to C^{k} \times \left\{ \vec{0} \right\}$ be defined
  by $G(u, \vec{0}) = \left( F(u), \vec{0} \right)$, we obtain
  %
  %
  \begin{gather*}
      \frac{dY}{dt} = G\left[ Y(z,t) \right]
      \\
      Y(0) = Y_{0}(z)
  \end{gather*}
%
where $Y_{0}(z) = Y_{0}(x, \tau)$ is a constant function of $\tau$. 
Applying Proposition \ref{prop:reg-result}, we obtain a solution $Y(z,t)$ which is
$C^{k}$ in $z$ locally in time. Since $z = (x, \tau)$, this implies that $Y(z,t)$ is
$C^{k}$ in $x$ and $\tau$, concluding the proof. 
%
\end{proof}
%
%
We are now prepared to prove the following. 
\begin{theorem}
  Let $U \subset C^{k}$ be an open subset, $k \ge 0$. Suppose $G: U \to C^{k}$ is Lipschitz
  and $k$ times differentiable. If $y_{0} \in C^{k}$, then
  there exists an open set $I \subset \rr$
such that the ivp 
\begin{gather}
\frac{dy}{dt} = G\left( y(x,t) \right)
\label{cc}
\\
y(0) = y_{0}(x), \quad x \in \ci^{n} \ \text{or} \ \rr^{n},t \in \rr
\label{dd}
\end{gather}
%
%
admits a unique solution $y(x,t)$ for $t \in I$. In addition,
this solution is $C^{k}$ in $x$ and $t$.
\label{thm:reg-result}
\end{theorem}
%
%
\begin{proof}
  We choose $F: U \times \rr \to C^{k}$ in \eqref{ode-param-naut}
  such that it is $C^{k}$ and satisfies 
  %
  %
  \begin{equation}
    \label{hjj}
  \begin{split}
    F\left[ y, \tau \right] = \tau F \left[ y, 1 \right].
  \end{split}
  \end{equation}
  %
  Note that \eqref{hjj} does not violate our assumption of $k$-differentiability
  for $F$, since
%
%
\begin{equation*}
\begin{split}
  DF\left[ y, \tau \right]
  & = \left( D_{y}(y, \tau) F, D_{\tau} F[y, \tau] \right)
  \\
  & = (  D_{y} \{\tau F[y, 1] \}, D_{\tau} \{F[y, 1] \} ) 
  \\
  & = ( \tau D_{y} F[y, 1], F[y, 1]).
\end{split}
\end{equation*}
%
%
Then if $y(x, t, \tau)$ is a solution to
\eqref{ode-param-naut}-\eqref{ode-param-init-naut}, we have $y(x, \tau, t ) =
y(x, 1, \tau t)$. To see this, note that
%
%
\begin{equation*}
\begin{split}
\frac{d}{dt}\left[ y(x, 1, \tau t) \right]
& = \tau y'(x, 1, \tau t)
\\
& = \tau F\left( 1, y(x, 1, \tau t) \right)
\\
& = F(\tau, y(x, 1, \tau t)).
\end{split}
\end{equation*}
%
%
That is, $y(x, 1, \tau t)$ is a solution
\eqref{ode-param-naut}-\eqref{ode-param-init-naut}. By uniqueness, $y(x, \tau, t) =
y(x, 1, \tau t)$. But formally, by the chain rule, we have
%
%
\begin{equation}
  \label{chain-comp}
\begin{split}
\frac{dy}{d \tau}(x, \tau, t) 
& = \frac{d}{d \tau}\left[ y(x, 1, \tau t) \right]
\\
& = \tau \frac{dy}{dt}\left[ y(x, 1, \tau t) \right] 
\end{split}
\end{equation}
%
%
By Corollary \ref{cor:reg-param}, $y$ is $C^{k}$ in $\tau$. Hence, from
\eqref{chain-comp}, we conclude that $y$ is $C^{k}$ in $t$. $C^{k}$
differentiability in $x$ follows from Corollary \ref{cor:reg-param}.
Running an induction, one obtains the corresponding result
for the case $k = \infty$. Lastly, for any given $G$, we can find $F$ satisfying
\eqref{hjj} and such that
$G(\cdot) = F(\cdot, 1)$. This concludes the proof.
%
\end{proof}
%
%
% \bib, bibdiv, biblist are defined by the amsrefs package.
\begin{bibdiv}
\begin{biblist}

\bib{Dieudonne_1969_Foundations-of-}{book}{
      author={Dieudonn{\'e}, J.},
       title={Foundations of modern analysis},
        date={1969},
         url={http://ams.org/mathscinet-getitem?mr=0349288},
}

\bib{Folland_1999_Real-analysis}{book}{
      author={Folland, Gerald~B.},
       title={Real analysis},
        date={1999},
  url={http://www.ams.org.proxy.library.nd.edu/mathscinet-getitem?mr=1681462},
}

\bib{Jost-1998-Postmodern-analysis}{book}{
      author={Jost, J{\"u}rgen},
       title={Postmodern analysis},
        date={1998},
  url={http://www.ams.org.proxy.library.nd.edu/mathscinet-getitem?mr=1490832},
}

\bib{Knapp:2005rm}{book}{
      author={Knapp, A.W.},
       title={Advanced real analysis},
   publisher={Birkhauser},
        date={2005},
        ISBN={0817643826},
}

\bib{Knapp:2005yg}{book}{
      author={Knapp, A.W.},
       title={Basic real analysis},
   publisher={Birkhauser},
        date={2005},
        ISBN={0817632506},
}

\bib{Rudin:1976uq}{book}{
      author={Rudin, Walter},
       title={Principles of mathematical analysis},
     edition={Third},
   publisher={McGraw-Hill Book Co.},
     address={New York},
        date={1976},
        note={International Series in Pure and Applied Mathematics},
}

\bib{Taylor:1995kx}{book}{
      author={Taylor, M.},
       title={Partial differential equations i, basic theory},
      series={Applied Mathematical Sciences},
   publisher={Springer-Verlag, New York},
        date={1995},
      volume={115},
}

\bib{Yosida:1980fk}{book}{
      author={Yosida, K{\^o}saku},
       title={Functional analysis},
     edition={Sixth},
      series={Grundlehren der Mathematischen Wissenschaften [Fundamental
  Principles of Mathematical Sciences]},
   publisher={Springer-Verlag},
     address={Berlin},
        date={1980},
      volume={123},
        ISBN={3-540-10210-8},
}

\end{biblist}
\end{bibdiv}
%
%
\bibliography{/Users/davidkarapetyan/math/bib-files/references.bib}
%\bibliographystyle{amsalpha}
\end{document}
