% Please use this sample.tex file.
%============================================
\documentstyle[12pt]{article}
\synctex=1
\renewcommand\floatpagefraction{0.9}
\renewcommand{\baselinestretch}{1.}
\topmargin 0.3in
\newcommand{\marg}[1]{\marginpar{\raggedright\scriptsize#1}}
\parskip=10pt
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{8.5in}
\setlength{\evensidemargin}{0.0in}
\setlength{\oddsidemargin}{0.0in}
\begin{document}
\pagestyle{empty}
\begin{center}
\begin{large}
{\bf Well-posedness and Propagation of Smoothness for
the Nonlinear Schr\"odinger Equation}
\end{large}
\end{center}

\vskip0.4in
\begin{center}
{\large \bf\underline{David Karapetyan}} \\
Department of Mathematics\\
University of Notre Dame\\
Notre Dame, IN 46556\\
E-mail: dkarapet@nd.edu\\
\end{center}



\bigskip
\centerline {{\bf ABSTRACT}}
\bigskip
\noindent
We consider the Cauchy problem for the nonlinear Schr{\"o}dinger equation and
prove well-posedness for initial data in various function spaces. Furthermore,
we discuss its analytic regularity in space and Gevrey regularity in time.



\providecommand{\bysame}{\leavevmode\hbox to3em{\hrulefill}\thinspace}
\providecommand{\MR}{\relax\ifhmode\unskip\space\fi MR }
% \MRhref is called by the amsart/book/proc definition of \MR.
\providecommand{\MRhref}[2]{%
  \href{http://www.ams.org/mathscinet-getitem?mr=#1}{#2}
}
\providecommand{\href}[2]{#2}
\begin{thebibliography}{1}

\bibitem{Bourgain-Fourier-transfo-1}
J.~Bourgain, \emph{Fourier transform restriction phenomena for certain lattice
  subsets and applications to nonlinear evolution equations. {I}.
  {S}chr{\"o}dinger equations}, Geom. Funct. Anal. \textbf{3} (1993), no.~2,
  107--156. 

\bibitem{Burq_Gerad_Tzvetkov-An-instability-}
N.~Burq, P.~G{{\'e}}rad, and N.~Tzvetkov, \emph{An instability property of the
  nonlinear {S}chr{\"o}dinger equation on {$S^d$}}, Math. Res. Lett. \textbf{9}
  (2002), no.~2-3, 323--335. 

\bibitem{Hannah:2006uq}
Heather Hannah, A.~Alexandrou Himonas, and Gerson Petronilho, \emph{Gevrey
  regularity in time for generalized {K}d{V} type equations}, Recent progress
  on some problems in several complex variables and partial differential
  equations, Contemp. Math., vol. 400, Amer. Math. Soc., Providence, RI, 2006,
  pp.~117--127. 

\bibitem{Himonas_Misioek-The-Cauchy-prob}
A.~Himonas and Gerard Misio{\l}ek, \emph{The {C}auchy problem for a shallow
  water type equation}, Comm. Partial Differential Equations \textbf{23}
  (1998), no.~1-2, 123--139. 

\end{thebibliography}
%\nocite{Himonas_Misioek-The-Cauchy-prob}
%\nocite{Bourgain-Fourier-transfo-1}
%\nocite{Hannah:2006uq}
%\nocite{Burq_Gerad_Tzvetkov-An-instability-}
%\bibliography{/Users/davidkarapetyan/math/bib-files/references.bib}
%\bibliographystyle{amsplain}
\end{document}
