%\ProvidesFile{template.tex}
\documentclass[final,noinfo]{nddiss2e}
                     % Available options are
                     % (a) draft + 10pt/11pt/12pt + twoadvisors + textrefs
                     % (b) review + noinfo + twoadvisors + textrefs
                     % (c) final + noinfo + twoadvisors + textrefs
%\let\bibsection\relax 

\usepackage{titlesec}
\titleformat{\chapter}[display]{\centering}
{\chaptertitlename\ \thechapter}{20pt}{\uppercase} %capitalize
%chapters--required by thesis format
\usepackage{titletoc}  %capitalize chapters in toc--required by thesis
\titlecontents{chapter}
[0pt]
{\addvspace{1pc}%
\normalfont}%
{\contentsmargin{0pt}%
\normalfont
\makebox[0pt][r]{\huge\thecontentslabel\enspace}%
\uppercase}
{\contentsmargin{0pt}%
\uppercase}
{\titlerule*[1pc]{.}\contentspage}
[\addvspace{0.1pc}]

\setcounter{tocdepth}{1} %must come before secnumdepth--else, pain
\setcounter{secnumdepth}{1} %number only sections, not subsections
\usepackage[T1]{fontenc}
\usepackage{appendix}
\usepackage{tikz}
\usepackage[utf8]{inputenc}
%\usepackage{showkeys}
\usepackage{lmodern} %this with above font packages give us all possible diacritics
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{appendix}
\usepackage{amssymb}
\usepackage{cancel}  %for cancelling terms explicity on pdf
\usepackage{yhmath}   %makes fourier transform look nicer, among other things
\usepackage{framed}  %for framing remarks, theorems, etc.
\usepackage{appendix}
\synctex=1
\usepackage{enumerate} %to change enumerate symbols
\usepackage[margin=2.5cm]{geometry}  %page layout
\setcounter{tocdepth}{1} %must come before secnumdepth--else, pain
\setcounter{secnumdepth}{1} %number only sections, not subsections
%\usepackage[initials]{amsrefs} %for the bibliography; uses cite pkg. Must be loaded after hyperref, otherwise doesn't work properly (conflicts with cref in particular)
\usepackage{hyperref}
\hypersetup{colorlinks=true,
linkcolor=blue,
citecolor=blue,
urlcolor=blue,
}
\usepackage{cleveref} %must be last loaded package to work properly
\renewcommand{\cref}{\Cref}
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{prop}[theorem]{Proposition}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{no}[theorem]{Notation}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}{Example}[section]
\newtheorem {exercise}[theorem] {Exercise}

\newcommand{\ds}{\displaystyle}
\newcommand{\ts}{\textstyle}
\newcommand{\nin}{\noindent}
\newcommand{\rr}{\mathbb{R}}
\newcommand{\nn}{\mathbb{N}}
\newcommand{\zz}{\mathbb{Z}}
\newcommand{\cc}{\mathbb{C}}
\newcommand{\ci}{\mathbb{T}}
\newcommand{\zzdot}{\dot{\zz}}
\newcommand{\wh}{\widehat}
\newcommand{\p}{\partial}
\newcommand{\ee}{\varepsilon}
\newcommand{\vp}{\varphi}
\newcommand{\wt}{\widetilde}
\renewcommand{\qed}{\qquad \qedsymbol}
\renewcommand{\chaptername}{CHAPTER}
\begin{document}

\frontmatter         % All the items before Chapter 1 go in ``frontmatter''

\title{ON THE WELL-POSEDNESS OF THE HYPERELASTIC ROD EQUATION}            % Title of Work
\author{David Karapetyan, B.S., M.S.}           % Author's name
\work{Dissertation}             % ``Dissertation'' or ``Thesis''
\degprior{}         % All prior degrees
\degaward{Ph.D}         % Degree you're aiming for
\advisor{Alex Himonas}          % Advisor's name
 % \secondadvisor{ } % Second advisor, if used option ``twoadvisors''
\department{Department of Mathematics, University of Notre Dame}       % Name of the department

\maketitle           % The title page is created now

 % \copyrightholder{ } % If you're not the copyright holder
 \copyrightyear{2011}   % If the copyright is not for the current year
\makecopyright      % If not making your work public domain
                       % uncomment out \makecopyright
 % \makepublicdomain   % Uncomment this to make your work public domain

\begin{abstract}
It is shown that the solution map for the hyperelastic rod equation is not
uniformly continuous on bounded sets of Sobolev spaces with exponent greater
than 3/2 in the periodic case and non-periodic cases. The proof is based on the
method of approximate solutions and well-posedness estimates for the solution
and its lifespan. Building upon this work, we also prove that the data to
solution map for the hyperelastic rod equation is H\"older continuous from
bounded sets of Sobolev spaces with exponent $s > 3/2$ measured in a weaker
Sobolev norm with exponent $r < s$ in both the periodic and non-periodic cases.
The proof is based on energy estimates coupled with a delicate commutator
estimate and multiplier estimate.
\end{abstract}
 %                         % Either place the text between begin/end, or
 % \include{abstract}  % put it in a file to be included

% \renewcommand{\dedicationname}{\mbox{}} % Replace \mbox{} if you want
                                           % something else
 \begin{dedication}
   \emph{To my mama. You have been patient. Be patient a little longer -- this is only the
   beginning.
   \\
To zemer Amelda, whose kindnesses
give me the strength to never bend, never break.
\\
To Cynthia -- loyal and fierce and loving until the end. 
}
  \end{dedication}
 %                       % Use one of the two choices to add dedication text
  %\include{dedication}

\tableofcontents
%\listoffigures
%\listoftables

 %% \renewcommand{\symbolsname}{newsymname} % Replace ``newsymname'' with
                                           % the name you want, and uncomment
 % \begin{symbols}
 % \end{symbols}
 %                       % Use one of the two choices to add symbols text
 % \include{symbols}

 %% \renewcommand{\prefacename}{ } % If you want another Preface name, add
                                   % something else, and uncomment
 % \begin{preface}
 % \end{preface}
 %                       % Use one of the two choices to add preface text
 % \include{preface}

 %% \renewcommand{\acknowledgename}{ } % If you want another Acknowledgement name
                                       % add something else, and uncomment
  \begin{acknowledge} I would like to thank my advisor, Professor Alex Himonas,
    for his support and guidance. I am also grateful to the math department and the  Arthur J. Schmitt
    Foundation for supporting my graduate studies. 

    Thanks also to Gerard Misio{\l}ek, who was always ready to answer the random
    analysis question or talk about the arts. To Professor Gerson Petronilho,
    for the many talks he has given, and his patience in collaborating with a
    junior mathematician. I am also indebted to my friend and collaborator
    Professor Dan Geba, who is one of the finest human beings I have ever
    known. He's also not too shabby at tennis. 

    Many thanks to my officemates Yen Huang and Wenrui Hao, who were always
    willing to discuss mathematics with me when we weren't horsing around. I
    must also thank Katie Grayshan for her friendship and many useful
    discussions, which helped me identify and shore up my weaknesses. 

    Thanks to Beth VerVelde, who understood me better than most, and is too
    wise for her own good. To my friends back home, thanks goes to Cynthia
    Ramirez, who always felt guilty whenever I was sent to voicemail, and
    called me back as soon as possible. Your patience and loyalty helped me
    persevere, and will not be forgotten. To Amelda zemer, your kindnesses and
    enormous heart have given me the strength to never break, no matter the
    adversity or general nonsense I may encounter.
    
    Lastly, thanks to my mom, Satenik Antonian, who has always had my best
    interests at heart, and has never wavered in her support and love. You have
    suffered more than most, yet take it stoically, with great grace, honor,
    and strength.    

    %The author thanks the Department of Mathematics at the University of Notre
    %Dame and the Arthur J. Schmitt Foundation for supporting his doctoral
    %studies.
  \end{acknowledge}
 %                       % Use one of the two choices to add acknowledge text
 % \include{acknowledgement}

\mainmatter
 % Place the text body here.
\include{./hr/hr}
\include{./hr/hr_holder_cont}
 %\input{./hr-holder/hr_holder_cont.tex}
%\appendix
%\include{./ode-thm/ode-thm}
 % If you have appendices, add them here.
 % Begin each one with \chapter{title} as before- the \appendix command takes
 % care of renaming chapter headings and creates a new page in the Table of
 % Contents for them.
 % \include{appendix-one}

\backmatter              % Place for bibliography and index
\begin{thebibliography}{35}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\bibitem[Bendahmane et~al.(2006)Bendahmane, Coclite, and
  Karlsen]{Bendahmane:2006p1301}
M.~Bendahmane, G.~M. Coclite, and K.~H. Karlsen.
\newblock \emph{Mediterr. J. Math.}, 3\penalty0 (3-4):\penalty0 419--432, 2006.

\bibitem[Benjamin(1972)]{Benjamin_1972_The-stability-o}
T.~B. Benjamin.
\newblock \emph{Proc. Roy. Soc. (London) Ser. A}, 328:\penalty0 153--183, 1972.

\bibitem[Benjamin et~al.(1972)Benjamin, Bona, and
  Mahony]{Benjamin_1972_Model-equations}
T.~B. Benjamin, J.~L. Bona, and J.~J. Mahony.
\newblock \emph{Philos. Trans. Roy. Soc. London Ser. A}, 272\penalty0
  (1220):\penalty0 47--78, 1972.

\bibitem[Bona and Tzvetkov(2009)]{Bona_2009_Sharp-well-pose}
J.~L. Bona and N.~Tzvetkov.
\newblock \emph{Discrete Contin. Dyn. Syst.}, 23\penalty0 (4):\penalty0
  1241--1252, 2009.

\bibitem[Bressan and Constantin(2007)]{Bressan_2007_Global-conserva}
A.~Bressan and A.~Constantin.
\newblock \emph{Arch. Ration. Mech. Anal.}, 183\penalty0 (2):\penalty0
  215--239, 2007.

\bibitem[Chen et~al.(2011)Chen, Liu, and Zhang]{Chen:2011fk}
R.~M. Chen, Y.~Liu, and P.~Zhang.
\newblock The H\"{o}lder Continuity of the Solution Map to the \$b\$-family
  Equation in weak topology.
\newblock Submitted, 2011.

\bibitem[Christ et~al.(2003)Christ, Colliander, and
  Tao]{Christ_2003_Asymptotics-fre}
M.~Christ, J.~Colliander, and T.~Tao.
\newblock \emph{Amer. J. Math.}, 125\penalty0 (6):\penalty0 1235--1293, 2003.

\bibitem[Coclite et~al.(2005)Coclite, Holden, and
  Karlsen]{Coclite_2005_Global-weak-sol}
G.~M. Coclite, H.~Holden, and K.~H. Karlsen.
\newblock \emph{SIAM J. Math. Anal.}, 37\penalty0 (4):\penalty0 1044--1069
  (electronic), 2005.

\bibitem[Constantin and Strauss(2000)]{Constantin_2000_Stability-of-a-}
A.~Constantin and W.~A. Strauss.
\newblock \emph{Phys. Lett. A}, 270\penalty0 (3-4):\penalty0 140--148, 2000.

\bibitem[Dai(1998)]{Dai_1998_Model-equations}
H.-H. Dai.
\newblock \emph{Acta Mech.}, 127\penalty0 (1-4):\penalty0 193--207, 1998.

\bibitem[Dai and Huo(2000)]{Dai_2000_Solitary-shock-}
H.-H. Dai and Y.~Huo.
\newblock \emph{R. Soc. Lond. Proc. Ser. A Math. Phys. Eng. Sci.}, 456\penalty0
  (1994):\penalty0 331--363, 2000.

\bibitem[Dai et~al.(2000)Dai, Dai, and Huo]{Dai_2000_Head-on-collisi}
H.-H. Dai, S.~Dai, and Y.~Huo.
\newblock \emph{Wave Motion}, 32\penalty0 (2):\penalty0 93--111, 2000.

\bibitem[Dieudonn{{\'e}}(1969)]{Dieudonne:1969}
J.~Dieudonn{{\'e}}.
\newblock \emph{Foundations of modern analysis}.
\newblock Academic Press, New York, 1969.
\newblock Enlarged and corrected printing, Pure and Applied Mathematics, Vol.
  10-I.

\bibitem[Herr et~al.(2010)Herr, Ionescu, Kenig, and Koch]{Herr:2010p886}
S.~Herr, A.~D. Ionescu, C.~E. Kenig, and H.~Koch.
\newblock \emph{Comm. Partial Differential Equations}, 35\penalty0
  (10):\penalty0 1827--1875, 2010.

\bibitem[Himonas and Kenig(2009)]{Himonas:2009fk}
A.~A. Himonas and C.~E. Kenig.
\newblock \emph{Differential Integral Equations}, 22\penalty0 (3-4):\penalty0
  201--224, 2009.

\bibitem[Himonas and Misio{\l}ek(2005)]{Himonas:2005}
A.~A. Himonas and G.~Misio{\l}ek.
\newblock \emph{Int. Math. Res. Not.}, \penalty0 (51):\penalty0 3135--3151,
  2005.

\bibitem[Himonas and Misio{\l}ek(2010)]{Himonas:2010a}
A.~A. Himonas and G.~Misio{\l}ek.
\newblock \emph{Comm. Math. Phys.}, 296\penalty0 (1):\penalty0 285--301, 2010.

\bibitem[Himonas and Misio{\l}ek(2001)]{Himonas_2001_The-Cauchy-prob}
A.~A. Himonas and G.~Misio{\l}ek.
\newblock \emph{Differential Integral Equations}, 14\penalty0 (7):\penalty0
  821--831, 2001.

\bibitem[Himonas et~al.(2007)Himonas, Misio{\l}ek, and
  Ponce]{Himonas_2007_Non-uniform-con}
A.~A. Himonas, G.~Misio{\l}ek, and G.~Ponce.
\newblock \emph{Asian J. Math.}, 11\penalty0 (1):\penalty0 141--150, 2007.

\bibitem[Himonas et~al.(2010)Himonas, Kenig, and Misio{\l}ek]{Himonas:2010}
A.~A. Himonas, C.~E. Kenig, and G.~Misio{\l}ek.
\newblock \emph{Comm. Partial Differential Equations}, 35\penalty0
  (6):\penalty0 1145--1162, 2010.

\bibitem[Holden and Raynaud(2007)]{Holden_2007_Global-conserva}
H.~Holden and X.~Raynaud.
\newblock \emph{J. Differential Equations}, 233\penalty0 (2):\penalty0
  448--484, 2007.

\bibitem[Karapetyan(2010)]{Karapetyan:2010fk}
D.~Karapetyan.
\newblock \emph{J. Differential Equations}, 249\penalty0 (4):\penalty0
  796--826, 2010.

\bibitem[Kato(1975)]{Kato:1975}
T.~Kato.
\newblock Quasi-linear equations of evolution, with applications to partial
  differential equations.
\newblock In \emph{Spectral theory and differential equations ({P}roc.
  {S}ympos., {D}undee, 1974; dedicated to {K}onrad {J}{\"o}rgens)}, pages
  25--70. Lecture Notes in Math., Vol. 448. Springer, Berlin, 1975.

\bibitem[Kenig et~al.(2001)Kenig, Ponce, and Vega]{Kenig_2001_On-the-ill-pose}
C.~E. Kenig, G.~Ponce, and L.~Vega.
\newblock \emph{Duke Math. J.}, 106\penalty0 (3):\penalty0 617--633, 2001.

\bibitem[Koch and Tzvetkov(2005)]{Koch:2005}
H.~Koch and N.~Tzvetkov.
\newblock \emph{Int. Math. Res. Not.}, \penalty0 (30):\penalty0 1833--1847,
  2005.

\bibitem[Lenells(2006)]{Lenells_2006_Traveling-waves}
J.~Lenells.
\newblock \emph{Discrete Contin. Dyn. Syst. Ser. B}, 6\penalty0 (1):\penalty0
  151--167 (electronic), 2006.

\bibitem[Li and Olver(2000)]{Li_2000_Well-posedness-}
Y.~A. Li and P.~J. Olver.
\newblock \emph{J. Differential Equations}, 162\penalty0 (1):\penalty0 27--63,
  2000.

\bibitem[Mustafa(2007)]{Mustafa:2007}
O.~G. Mustafa.
\newblock \emph{Int. Math. Res. Not. IMRN}, \penalty0 (13):\penalty0 Art. ID
  rnm040, 26, 2007.

\bibitem[Olson(2006)]{Olson_2006_Non-uniform-dep}
E.~Olson.
\newblock \emph{Differential Integral Equations}, 19\penalty0 (10):\penalty0
  1081--1102, 2006.

\bibitem[Rodr\'iguez-Blanco(2001)]{Rodriguez-Blanco_2001_On-the-Cauchy-p}
G.~Rodr\'iguez-Blanco.
\newblock \emph{Nonlinear Anal.}, 46\penalty0 (3, Ser. A: Theory
  Methods):\penalty0 309--327, 2001.

\bibitem[Tao(2004)]{Tao:2004}
T.~Tao.
\newblock \emph{J. Hyperbolic Differ. Equ.}, 1\penalty0 (1):\penalty0 27--49,
  2004.

\bibitem[Taylor(1991)]{Taylor:1991}
M.~E. Taylor.
\newblock \emph{Pseudodifferential operators and nonlinear {PDE}}, volume 100
  of \emph{Progress in Mathematics}.
\newblock Birkh{\"a}user Boston Inc., Boston, MA, 1991.

\bibitem[Taylor(2011)]{Taylor:2011}
M.~E. Taylor.
\newblock \emph{Partial differential equations {I}. {B}asic theory}, volume 115
  of \emph{Applied Mathematical Sciences}.
\newblock Springer, New York, second edition, 2011.

\bibitem[Yin(2003)]{Yin_2003_On-the-Cauchy-p}
Z.~Yin.
\newblock \emph{J. Nonlinear Math. Phys.}, 10\penalty0 (1):\penalty0 10--15,
  2003.

\bibitem[Zhou(2005)]{Zhou_2005_Local-well-pose}
Y.~Zhou.
\newblock \emph{Math. Nachr.}, 278\penalty0 (14):\penalty0 1726--1739, 2005.

\end{thebibliography}
%\bibliographystyle{nddiss2e}
%%\bibliographystyle{amsalpha-custom} 
%\bibliography{/Users/davidkarapetyan/math/bib-files/references}

\end{document}

%%
\endinput
%%
